---
title: "Modelling for RSV"
author: "Phuong Huynh Thi"
date: "24/03/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Setting
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())
setwd("/home/phuong/phuonght/gitKraken_project/RSV")
library(deSolve)
library(ggplot2)

#Changeable variables  ##########################
#vaccinnation coverage = c+c1 ( 40%, 80%,): 
coverage = 0.8   # 0.2,0.4,0.6,0.8
c = coverage*1/2   # vaccinate a fraction p of newborn 
c1= coverage-c       # vaccinate a fraction p of AG1 ( aged< 1 year)
e = 0.7              # vaccine efficacy is 70%
t_shift = 401        # optimized from fitting# this change up to what fitted set of params
t_vac = 9          # wk29,33,37## vaccinating 3,2,1 month before the epidemic season starts at week 41st till the end of the season at wk 8 next year
vac_str = "year-round" # year-round or seasonal # vaccination strategy will be applied.

#vaccine duration: 32, 28, 24 and 52 weeks are generalized as below:
if(vac_str=="year-round"){
 vac_period = 52 
}else{
  vac_period <- (52-t_vac+1+8)  # start vaccination from week 't_vac" this year to week 8 next year # 
}

report_rate <- 0.675   #assuming only 67.5% of RVS incidence are reported with those aged < 1

# Re-calculate the coverage 
#this code below limit c1 < 1 !!!!!!!!!!!
if (c==1) { # avoid denominator =0 !
  p1 <- 0
  p  <- c*52/vac_period
  if(p > 1){ # set the limit for p<=1
    p <-1
  }else{
    p  <- c*52/vac_period
  }
}else{
  p1 <- (-log(1-(c1/(1-c)))/vac_period) # c1/(1-c): coverageAG1, -log: S reduce by time
  p  <- c*52/vac_period
  if(p > 1){ # set the limit for p<=1
    p <-1
  }else{
    p  <- c*52/vac_period
  }
}

real_cov <- p/(52/vac_period) + c1
real_cov

```
Notes:
The coverage value will be transformed into faction p(<1) and p1 in the dynamic model. if p>1,set p =1 , meaning that the coverage is not hold => recal calculate it for CEA analysis later 

# Parameters
```{r}
######################################### #
# POPULATION AND PARAMETERS  ----
######################################### #
#https://steemit.com/science/@fouad/x-history-of-math-symbols
pop_size          <- 11176549# Belgium pop size (average 2011-2018)
ag1_size          <- pop_size*1/80
ag2_size          <- pop_size - ag1_size
num_days          <- 500
num_weeks         <- 52*30
num_days_infected <- 10  #[ 8-11], 6.7 is original estimate
num_days_exposed  <- 4   # [2,6]
num_days_waning   <- 200 # [148, 164] best fit
infected_seeds    <- 100# ? 1= 1000 1% of children ??? 

# the fitted parameters may be different between population size
  # set parameters
  params     <- c(sigma = 7/num_days_exposed,  #latent to infectious stage
                  # sigma = 1/0.57,              # latent to infectious stage
                  gamma = 7/num_days_infected,# recovery rate
                  # gamma = 1/1.4,               # recovery rate
                  # nu=  7/num_days_waning,     # rate of loss of immunity
                  nu   =  0.03,                  # rat e of loss of immunity
                  eta1 = 1/(1*52),             # aging rate AG1
                  eta2 = 1/(79*52),            # aging rate AG2
                  mu   = 1/(80*52),              # birth rate
                  a    = 0.899,                    # the degree of seasonality, range [0,1]
                  phi  = 4,                 # phase shift?
                  b    = 1.84,                   #average transmission rate
                  delta = 0.65,                # scaled susceptibility
                  alpha = 0.65                 # scaled infectiousness
  )
# Best fit parameter:
  # plot_model_fit(c(log(1.84),log(0.899),log(4),log(401),log(0.03))) # 6181.19
#Calculate R0?!1/
##https://web.stanford.edu/~jhj1/teachingdocs/Jones-on-R0.pdf
  #R0 = trans_rate*infec_rate*birth_rate/(infec_rate + death_rate)*(recover_rate + death_rate)*death_rate
b <- 1.84
  # R0 <- b*sigma/(sigma+mu)*(gamma+mu)
R0 <- params["b"]*params["sigma"]/((params["sigma"] + params["mu"])*(params["gamma"] + params["mu"]))
R0
  
```

# SEIRS with differnt intervention scenarios.
*Vaccination period*
 - Seasonal : 1 or 2 months befor the season start
 - year-round
*Vaccination target*
 - newborn (maternal)
 - infant ( aged < 1)
 - both
*Vaccine coverage*
 - 40%
 - 80%
```{r Model structure, echo=T, eval=T}
#eval = F: preventing running codes

  #sum total population =1
  S1 <- 1/80 # less than 1 yrs old
  E1 <- (infected_seeds*0.7)/(pop_size)
  I1 <- 0
  R1 <- 0
  V1  <- 0
  E2 <- (infected_seeds*0.3)/(pop_size) # greater than 1 yrs old
  I2 <- 0
  R2 <- 0
  S2 <- 1-S1-E1-I1-R1-E2-I2-R2-V1 

######################################### #
# SET FUNCTION PARAMETERS            ----
######################################### #
# set time frame
times      <- seq(0, num_weeks, by = 1)
# set initial health states
states     <- c(S1 = S1,E1 = E1, I1 = I1, R1 = R1, V1 = V1,
                S2 = S2,E2 = E2, I2 = I2, R2 = R2)
######################################### #
# CREATE SIRV FUNCTION               ----
######################################### #
# Note: updating the health states over time and keeping track of the changes, is handled by the
# ode-function of the 'deSolve' package.
sirv_func <- function(t, states, params) {
  
  with(as.list(c(states, params)),
       {
         # define variables
         beta <- b*(1+a*cos(2*pi*t/52+phi))
         
         if(vac_str=="year-round"){
           # vaccinate year-round
           if(t<(t_shift+33)){#start vaccination at week 33 and contiunue year-round
             p  <- 0
             p1 <- 0
           } else if (c==1) { # avoid denominator =0
             p1 <- 0
             p  <- c*52/vac_period
             if(p > 1){ # set the limit for p<=1
               p <-1
             }else{
               p  <- c*52/vac_period
             }
           }else{
             p1 <- (-log(1-(c1/(1-c)))/vac_period) # c1/(1-c): coverageAG1
             p  <- c*52/vac_period
             if(p > 1){ # set the limit for p<=1
               p <- 1
             }else{
               p  <- c*52/vac_period
             }
           }
         }
           
         if(vac_str=="seasonal"){
           # Vaccinate seasonal: 3,2,1 months before the the epidemic season start
           if(t< (t_shift+t_vac)){# skip 't_vac' wks of 
             p  <- 0
             p1 <- 0
           }
           if(t>= (t_shift +t_vac)){# start vaccination epidemic season 2011/2012
             t_week = (t-t_shift)%%52
             if(floor(t_week) >= t_vac|floor(t_week) <= 8){
               if(c==1){# avoid denominator =0 !
                 p1 <- 0
                 p  <- c*52/vac_period  # scaling dose if vaccination time is shorter?
                 if(p>1){ # set the limit for p<=1
                   p <- 1
                 }else{
                   p <- c*52/vac_period
                 }
               }else{
                 p1 <- (-log(1-(c1/(1-c)))/vac_period) # c1/(1-c): coverageAG1
                 p  <- c*52/vac_period  # scaling dose if vaccination time is shorter?
                 if(p>1){ # set the limit for p<=1
                   p <-1
                 }else{
                   p  <- c*52/vac_period
                 }
               }
             }else{
               p  <- 0
               p1 <- 0
             }
           } 
         }
         
         # calculate state changes
         dS1 <- (1-p*e)*mu  - beta*S1*(I1+alpha*I2)  + nu*R1                - eta1*S1 - p1*e*S1
         dE1 <-               beta*S1*(I1+alpha*I2)  - sigma*E1             - eta1*E1
         dI1 <-                                        sigma*E1  - gamma*I1 - eta1*I1
         dR1 <-                                      - nu*R1     + gamma*I1 - eta1*R1 
         
         dV1 <- p*e*mu - eta1*V1 + p1*e*S1
         
         dS2 <- eta1*V1 +eta1*S1 - delta*beta*S2*(I1+alpha*I2) + nu*R2                - eta2*S2 
         dE2 <-          eta1*E1 + delta*beta*S2*(I1+alpha*I2) - sigma*E2             - eta2*E2 
         dI2 <-          eta1*I1                               + sigma*E2 - gamma*I2  - eta2*I2 
         dR2 <-          eta1*R1                               - nu*R2    + gamma*I2  - eta2*R2 
         
         # return (dS, dI, dR) as a vector in a list (required for the 'solve' function)
         return(list(c(dS1, dE1, dI1, dR1,dV1, dS2, dE2, dI2, dR2)))
       }
  )
}


```

#ODE
```{r ODE, echo=T, eval=T}
#eval = F: preventing running codes
######################################### #
# SOLVE ODE                          ----
######################################### #
# use the 'ode' function of deSolve package with our SIR function, health states and parameters
out <- ode(func = sirv_func, y = states, times = times, parms = params)
# plot(out)
# summary(out)
# times_output <- seq(num_weeks-(52*8)-2,num_weeks,1)# burning time ## shifting peaks
times_output <- seq(num_weeks-(num_weeks-t_shift),num_weeks,1)# burning time ## shifting peaks
# times_output <- times_output[1:346]# take exactly 8 years (378-32 wks) for later fitting data
times_output <- times_output[1:(52*11)]# show model in 11 yrs
out <- out[out[,1] %in% times_output,] # skip the initial time points
out[,1] <- out[,1] - min(out[,1]-1)# rescale time points ## -1: first week is 1
######################################### #
# PLOT RESULTS                       ----
######################################### #
# convert the 'out' matrix into a data-frame (to enable the use of '$' to access a column by name)
out <- as.data.frame(out)
out$S <- out[,"S1"] + out[,"S2"]
out$E <- out[,"E1"] + out[,"E2"]
out$I <- out[,"I1"] + out[,"I2"]
out$R <- out[,"R1"] + out[,"R2"]
out$V <- out[,"V1"]
pop <- out$S + out$E +out$I + out$R + out$V



##Number of infection each epidemic year : week 33 to week 32 next year:
ag1_est_year1 <- sum(floor(out$I1[33:(33+51)]*pop_size))#year 2011-2012
ag1_est_year2 <- sum(floor(out$I1[85:(85+51)]*pop_size))
ag1_est_year3 <- sum(floor(out$I1[137:(137+51)]*pop_size))
ag1_est_year4 <- sum(floor(out$I1[189:(189+51)]*pop_size))
ag1_est_year5 <- sum(floor(out$I1[241:(241+51)]*pop_size))
ag1_est_year6 <- sum(floor(out$I1[293:(293+51)]*pop_size))
ag1_est_year7 <- sum(floor(out$I1[345:(345+51)]*pop_size))
ag1_est_year8 <- sum(floor(out$I1[397:(397+51)]*pop_size))
ag1_est_year9 <- sum(floor(out$I1[449:(449+51)]*pop_size))
ag1_est_year10 <- sum(floor(out$I1[501:(501+51)]*pop_size))

case <- data.frame(c(ag1_est_year1,
                    ag1_est_year2,
                    ag1_est_year3,
                    ag1_est_year4,
                    ag1_est_year5,
                    ag1_est_year6,
                    ag1_est_year7,
                    ag1_est_year8,
                    ag1_est_year9,
                    ag1_est_year10))


case$year <- seq(1:10)
colnames(case)      <- c("case","year")
#Add other variables
case$coverage <- coverage
case$real_cov <- rep(real_cov,10)
case$c        <-c
case$c1       <-c1
case$vac_str  <- vac_str
case$vac_week <- t_vac

#Total number of infections
ag1_est <- floor(out$I1[33:552]*pop_size)# 10 epidemic years
ag1_est_10yr <- sum(ag1_est)
ag1_est_378wk <-sum(floor(out$I1[1:378]*pop_size))
#saving file
# if(vac_str=="seasonal"){
#   write.csv(case, paste("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/estimated_case/case.est c=",c,"c1=",c1,vac_str,"wk",t_vac,".csv"),row.names = F)
# }
# if(vac_str=="year-round"){
#   write.csv(case, paste("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/estimated_case/case.est c=",c,"c1=",c1,vac_str,".csv"),row.names = F)
# }


#BELGIUM DATA-----------------
case_dt <- read.csv("./RSV data/RSV_cases_time_epistat.csv")
case_dt$week      <- seq(1,dim(case_dt)[1])
age_dt <- read.csv("./RSV data/RSV_cases_age_epistat.csv")
# total cases: 63301,4yrs: 822,3yr:1794,2yr:4559 1yr:13751,0yr:42375
pro.less1yr  <- age_dt$cases[age_dt$age==0] / sum(age_dt$cases) 
case_dt$cases_ag1 <- round(case_dt$cases*pro.less1yr)
case_dt$cases_ag2 <- case_dt$cases - case_dt$cases_ag1
#Assuming only 67.5% incidence was reported
case_dt$cases_scaled <- round(case_dt$cases/0.675)
case_dt$cases_ag1_scaled <- round(case_dt$cases_ag1/0.675)
case_dt$cases_ag2_scaled <- case_dt$cases_scaled - case_dt$cases_ag1_scaled
  
######################################### #
# Plot Model fit                      ----
######################################### #
# plot real data
par(mfrow = c(1,1))
plot(case_dt$week, # plot seasonal 
     case_dt$cases_ag1,
     xlab = "Time (weeks)",
     ylab = "Number of RSV reported (age<1)",
     pch=19,col=1,
     ylim = c(0, max(case_dt$cases_ag1)*1.2),
     xaxt="none")# for later customizing
axis(1,seq(0,350,by=50))# customize x-axis
# plot initial model
lines(out$time[1:length(case_dt$cases_ag1)],out$I1[1:length(case_dt$cases_ag1)]*pop_size*report_rate,col=2,lwd=2,type = "b",pch=1)
legend(315,1200, legend = c("observed","model fit"), col = c(1,2),lty=1:2,pch=c(19,1))


# Vaccination effect:
par(mfrow = c(1,1))
plot(out$time, # plot seasonal
     out$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     main= paste("Vaccination c =",c,"c1=",c1,vac_str,"wk",t_vac),col=2,type = "l",lwd=2,
     xlim = c(0,52*10),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))

# # Vaccination effect
# if(coverage==0){
# out1 <-out
# }
# if(coverage==0.4){
# out4 <-out
# }
# if(coverage==0.8){
# out8 <-out
# }
# 
# par(mfrow = c(1,1))
# plot(out1$time, # plot seasonal
#      out1$I1*pop_size,
#      xlab = "Year",
#      ylab = "Number of RSV infection",
#      # main= paste("Vaccination fraction =",p),
#      col=1,type = "l",lwd=2,
#      xlim = c(0,52*10),
#      ylim = c(0,1300),
#      xaxt="none")# for later customizing
# axis(1, at=seq(0,520,by=52),labels = c(0:10))
# lines(out4$time,out4$I1*pop_size,col=2,lwd=2,type = "l",lty=2)
# lines(out8$time,out8$I1*pop_size,col=3,lwd=2,type = "l",lty=3)
# legend(370,1350, legend = c("no intervention","40% vaccinated","80% vaccinated"),
#        col = c(1,2,3),lty=c(1,2,3))


```

# Optimizing parameters
##original report data 
###Least square

```{r Fitting, echo=T, eval=F}
#eval = F: preventing running codes
######################################### #
# Parameters optimizations                      ----
######################################### #
# DEFINE HELP FUNCTION TO CALCULATE SUM OF SQUARES
get_sum_of_squares <- function(model_values,ref_values) {
  return(sum(sqrt((model_values-ref_values)^2)))
}
# SET GOAL: to use the optimisation package
library(Rcpp)
library(optimization)
#DEFINE FUNCTION TO RUN ODE WITH PARAMETER VECTOR X
x <- c(1.82, 0.76,2.8,461,0.03) #b[?] a(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days
get_model_output <- function(x){
  # params_fitting
  params_fit = params
  params_fit["b"] = x[1]
  params_fit["a"] = x[2]
  params_fit["phi"] =   x[3]
  time_shift =x[4]
  params_fit["nu"] = x[5]
  # get output
  out <- data.frame(ode(func = sirv_func, y = states, times = seq(0,num_weeks,1), parms = params_fit))
  # shift in time (fill with 0)
  out <- approx(x   = out$time - time_shift,
                y   = out$I1,
                xout = seq(0,num_weeks,1), # only extract y where x in this seq
                rule = 1)  # NAs is returned as it is
  names(out) <- c('time','I1')
  # rescale time points
  out$time <- out$time - min(out$time)
  # return output
  return(out)
}
# HELP FUNCTION TO CALCULATE SUM OF SQUARES GIVEN PARAMETERS 'X'
get_parameter_score <- function(x) {
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  # get model score
  model_score <- get_sum_of_squares(model_out$I1*pop_size,case_dt$cases_ag1)
  # return model score
  return(model_score)
}
# HELP FUNCTION TO VISUALIZE THE MODEL FITTING
plot_model_fit <- function(x){
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  # get model score
  model_score <- get_sum_of_squares(model_out$I1[1:length(case_dt$cases)]*pop_size,case_dt$cases_ag1)
  # plot reference data
  plot(case_dt$week,
       case_dt$cases_ag1,
       ylim = c(0,max(case_dt$cases_ag1)*2),type = "b",pch=19,
       main = paste('score:',round(model_score,digits = 2)))
  # plot initial model
  lines(model_out$time,model_out$I1*pop_size,col=2,lwd=1,type = "b")
}
#Optimizing parameters, by specifing lower and upper values
beta0[?] beta1(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days
opt_param_sa <- optim_sa(fun = get_parameter_score, start = c(1.8,0.1,1,-200,7/350),
                         trace = FALSE,
                         lower = c(1,0,1,-1000,7/350),#
                         upper = c(3,1,3,-100,7/160),
                         control = list(dyn_rf = F,
                                        rf = 1,
                                        t0 = 1000, nlimit = 100, r = 0.6, t_min = 0.1
                         ))$par

opt_param_sa
plot_model_fit(opt_param_sa)
################################# #
#report data 100%----------------
################################# #
# sigma = 1/0.57,gamma = 1/1.4
    # plot_model_fit(c(1.85,0.85,3.1,-357,0.032)) #21605.41
  #sigma = 7/num_days_exposed, gamma = 7/num_days_infected
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.038)) # 20915.97
   # plot_model_fit(c(1.82,0.875,3.1,-462,0.034))# 22313.57
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.039)) # 23207.43
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.036)) # 24552.02
   # plot_model_fit(c(1.82,0.88,3.1,-461,0.037)) # 18337.04 # consider
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.037)) # 21000.11
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.039)) # 23207.43 #
   # plot_model_fit(c(1.82,0.87,3.1,-462,0.036)) # 23207.43 #
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.036)) # 24552.02
   

```

## 67.5% Scaling report data 
### Least square
Assuming 67.5% RSV cases are reported as the same rate of rotavirus.

```{r Fitting, echo=T, eval=F}
#eval = F: preventing running codes

######################################### #
# Parameters optimizations                      ----
######################################### #
# DEFINE HELP FUNCTION TO CALCULATE SUM OF SQUARES
get_sum_of_squares <- function(model_values,ref_values) {
  return(sum(sqrt((model_values-ref_values)^2)))
}
# SET GOAL: to use the optimisation package
library(Rcpp)
library(optimization)
#DEFINE FUNCTION TO RUN ODE WITH PARAMETER VECTOR X
x <- c(1.82, 0.76,2.8,515,0.03) #b[?] a(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days
get_model_output <- function(x){
  # params_fitting
  params_fit = params
  params_fit["b"] = x[1]
  params_fit["a"] = x[2]
  params_fit["phi"] =   x[3]
  time_shift =x[4]
  params_fit["nu"] = x[5]
  # get output
  out <- data.frame(ode(func = sirv_func, y = states, times = seq(0,num_weeks,1), parms = params_fit))
  # shift in time (fill with 0)
  out <- approx(x   = out$time - time_shift,
                y   = out$I1,
                xout = seq(0,num_weeks,1),
                rule = 1) # NAs is returned as it is
  names(out) <- c('time','I1')
  # rescale time points
  out$time <- out$time - min(out$time)
  # return output
  return(out)
}
# HELP FUNCTION TO CALCULATE SUM OF SQUARES GIVEN PARAMETERS 'X'
get_parameter_score <- function(x) {
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  
  ###############
  # COMPARING THE MODEL OUTPUT WITH DATA for each combination (optional)
  plot(case_dt$week,
       case_dt$cases_ag1,
       ylim = c(0,max(case_dt$cases_ag1)*1.2),type = "b",pch=19)
  ## plot initial model
  lines(model_out$time,model_out$I1*pop_size*report_rate,col=2,lwd=1,type = "b")
  ################
  
  # get model score
 model_score <- get_sum_of_squares(model_out$I1[1:length(case_dt$cases_ag1)]*pop_size*report_rate,case_dt$cases_ag1)
  # return model score
  return(model_score)
}
#OPTIMIZING PARAMETERS, by specifing lower and upper values
beta0[?] beta1(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days
fit <- optim_sa(fun = get_parameter_score, start = c(1.8,0.65,3.15,200,7/200),
                trace = FALSE,
                lower = c(1.7,0.1,3,50,7/230),#
                upper = c(2,0.9,4,600,7/160),
                control = list(dyn_rf = F,
                               rf = 1,
                               t0 = 1000, nlimit = 100, r = 0.6, t_min = 0.1
                ))

fit$par

# fit<-optim(c(1.81,0.84,3.4,200,7/200),
#            fn = get_parameter_score,
#            lower = c(1.8,0.8,3.2,100,7/230),#
#            upper = c(2,0.9,4,400,7/160),
#            hessian = TRUE,method=("L-BFGS-B"),
#            control = list(trace=TRUE, maxit=100))
# fit$par

# HELP FUNCTION TO VISUALIZE THE MODEL FITTING
plot_model_fit <- function(x){
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  # get model score
  model_score <- get_sum_of_squares(model_out$I1[1:length(case_dt$cases_ag1)]*pop_size*report_rate,case_dt$cases_ag1)
  # plot reference data
  plot(case_dt$week,
       case_dt$cases_ag1,
       ylim = c(0,max(case_dt$cases_ag1)*2),type = "b",pch=19,
       # xlim=c(0,500),
       main = paste('LS:',round(model_score,digits = 2),
                    "b:",opt_param_sa[1],
                    "a:",opt_param_sa[2],
                    "phi:",opt_param_sa[3],
                    "t_shift:",opt_param_sa[4],
                    "nu:",opt_param_sa[5]))
  # plot initial model
  lines(model_out$time,model_out$I1*pop_size*report_rate,col=2,lwd=1,type = "b")
}

plot_model_fit(fit$par)


# [1]   1.813   0.845   3.280 199.060   0.035 # 17662.05
# [1]   1.833   0.885   3.100 200.780   0.035 # 17318.9

  
```

### Poisson likelihood

```{r Fitting, echo=T, eval=F}
#eval = F: preventing running codes

######################################### #
# Parameters optimizations                      ----
######################################### #

# SET GOAL: to use the optimisation package
library(Rcpp)
library(optimization)
#DEFINE FUNCTION TO RUN ODE WITH PARAMETER VECTOR X
x <- c(log(1.82),log( 0.88),log(3.1),log(461), log(0.037)) #b[?] a(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days
get_model_output <- function(x){
  # params_fitting
  params_fit = params
  params_fit["b"] = exp(x[1])
  params_fit["a"] = exp(x[2])
  params_fit["phi"] =   exp(x[3])
  time_shift = exp(x[4])
  params_fit["nu"] = exp(x[5])
  # get output
  out <- data.frame(ode(func = sirv_func, y = states, times = seq(0,num_weeks,1), parms = params_fit))
  # shift in time (fill with 0)
  out <- approx(x   = out$time - time_shift,
                y   = out$I1,
                xout = seq(0,num_weeks,1),
                rule = 1) # NAs is returned as it is
  names(out) <- c('time','I1')
  # rescale time points
  out$time <- out$time - min(out$time)
  # return output
  return(out)
}


# HELP FUNCTION TO CALCULATE Negative log likelihood GIVEN PARAMETERS 'X'
get_parameter_score <- function(x) {
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  
  ###############
  # COMPARING THE MODEL OUTPUT WITH DATA for each combination (optional)
  plot(case_dt$week,
       case_dt$cases_ag1,
       ylim = c(0,max(case_dt$cases_ag1)*1.2),type = "b",pch=19)
  ## plot initial model
  lines(model_out$time,model_out$I1*pop_size*report_rate,col=2,lwd=1,type = "b")
  ################
  
  L<-matrix(0,nrow=length(case_dt$cases),ncol=1)
  
  #Obtains the likelihood from the model
  L<-dpois(case_dt$cases_ag1,model_out$I1[1:length(case_dt$cases_ag1)]*pop_size*report_rate,log=TRUE)
  
  #Log likelihood
  LL<-sum((1-(L==-Inf))*L,na.rm=TRUE)
  
  #Negative log likelihood
  NLL<--LL
  
  # return model score
  return(NLL)
}

#OPTIMIZING PARAMETERS, by specifing lower and upper values, by specifing lower and upper values
# beta0[?] beta1(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days

set.seed(9)
fit<-optim(c(log(1.85),log(0.85),log(3.1),log(200),log(7/200)),
           fn = get_parameter_score,
           lower = c(log(1.84),log(0.8),log(3),log(100),log(7/230)),
           upper = c(log(1.9),log(0.9),log(4),log(400),log(7/160)),
           hessian = TRUE,method=("L-BFGS-B"),
           control = list(trace=TRUE,factr=1e-8))

par <- round(exp(fit$par),3)
par



# HELP FUNCTION TO VISUALIZE THE MODEL FITTING
plot_model_fit <- function(x){
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  # get model score POSSON LOG LIKELIHOOD
  L<-matrix(0,nrow=length(case_dt$cases),ncol=1)
  
  #Obtains the likelihood from the model
  L<-dpois(case_dt$cases_ag1,model_out$I1[1:length(case_dt$cases)]*pop_size*report_rate,log=TRUE)
  
  #Log likelihood
  LL<-sum((1-(L==-Inf))*L,na.rm=TRUE)
  
  #Negative log likelihood
  NLL<--LL
  model_score <- NLL
  
  # plot reference data
  plot(case_dt$week,
       case_dt$cases_ag1,
       ylim = c(0,max(case_dt$cases_ag1)*1.2),type = "b",pch=19,
       # xlim=c(0,500),
       main = paste('NLL:',round(model_score,digits = 2),
                                 "b:",par[1],
                                 "a:",par[2],
                                 "phi:",par[3],
                                 "t_shift:",par[4],
                                 "nu:",par[5]))
  # plot initial model
  lines(model_out$time,model_out$I1*pop_size*report_rate,col=2,lwd=1,type = "b")
}

plot_model_fit(fit$par)
# plot_model_fit(c(log(1.84),log(0.899),log(4),log(400),log(0.03))) # 7936.4
# plot_model_fit(c(log(1.84),log(0.899),log(4),log(402),log(0.03))) # 7755
# plot_model_fit(c(log(1.84),log(0.899),log(4),log(401),log(0.03))) # 6181.19


#[1]  0.6004835 -0.1221676  1.3674025  5.8583174 -3.2601691 #NLL:6863.6
 # ~ 1.82300000   0.88500000   3.92514170 350.13450006   0.03838191
#1.81809030  0.82631195  3.96459003 90.76895906  0.03642838
# [1]   1.87345939   0.97943156   2.99637269 254.24983006   0.03329303 
# [1]   1.83636241   0.85147689   3.34478512 458.66374805   0.03570705
#[1]   1.91130578  0.99921739  3.44664899 95.42278310  0.03679449

################################# #
#calculating the confidence intervals for the parameter estimates:
##################################

fisher_info <- solve(fit$hessian)
prop_sigma <- sqrt(diag(fisher_info))
upper <- exp(fit$par+1.96*prop_sigma)
upper
lower <- exp(fit$par-1.96*prop_sigma)
lower
estimate <- exp(fit$par)
estimate
  
```

"These are warnings that result from R searching in parameter values that makedpoisreturn not-a-number (NaN) errors.  In other words, if R tries a value the mean of the poisson distribution thatis negative, then R can’t compute a probability for that, because a negative mean is impossible forcounts.  So dpois informs mle2 of this, and then you see a warning, and R goes back to searchingat other parameter values"


#Vaccination effect
```{r, eval=F }
#eval = F: preventing running codes
#The rm(list=ls()) should be off to run and store all these subjects below in the enviroment 

# Change the name of "out" output with each scenarios
if(coverage==0){
  out1 <-out
}
if(coverage==0.4){
  if(c==0.4 & vac_str=="year-round"){
    out4_yr.nb <- out
  }
  if(c1==0.4 & vac_str=="year-round"){
    out4_yr.AG1 <- out
  }
  if(c==0.2 & vac_str=="year-round"){
    out4_yr.both <- out
  }
  if(c==0.4 & vac_str=="seasonal"& t_vac==33){
    out4_wk33.nb <- out
  }
  if(c1==0.4 &vac_str=="seasonal"& t_vac==33){
    out4_wk33.AG1 <- out
  }
  if(c==0.2 &vac_str=="seasonal"& t_vac==33){
    out4_wk33.both <- out
  }
  if(c==0.4 &vac_str=="seasonal"&t_vac==37){
    out4_wk37.nb <- out
  }
  if(c1==0.4 &vac_str=="seasonal"& t_vac==37){
    out4_wk37.AG1 <- out
  }
  if(c==0.2 &vac_str=="seasonal"& t_vac==37){
    out4_wk37.both <- out
  }
} 
if(coverage==0.8){
  if(c==0.8&vac_str=="year-round"){
    out8_yr.nb <- out
  }
  if(c1==0.8&vac_str=="year-round"){
    out8_yr.AG1 <- out
  }
  if(c==0.4&vac_str=="year-round"){
    out8_yr.both <- out
  }
  if(c==0.8 &vac_str=="seasonal"&t_vac==33){
    out8_wk33.nb <- out
  }
  if(c1==0.8 & vac_str=="seasonal"&t_vac==33){
    out8_wk33.AG1 <- out
  }
  if(c==0.4 &vac_str=="seasonal"& t_vac==33){
    out8_wk33.both <- out
  }
  if(c==0.8 &vac_str=="seasonal"&t_vac==37){
    out8_wk37.nb <- out
  }
  if(c1==0.8&vac_str=="seasonal"& t_vac==37){
    out8_wk37.AG1 <- out
  }
  if(c==0.4 &vac_str=="seasonal"& t_vac==37){
    out8_wk37.both <- out
  }
}

#plot multiple plots in one page
par(mfrow=c(3,3), tcl=-0.6, family="serif", mai=c(0.25,0.25,0.25,0.25)) # reduce gap between plots

# par(mfrow = c(3,3))
#year-round
##nb
plot(out1$time, # plot seasonal
     out1$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     # main= paste("Vaccination fraction =",p),
     col=1,type = "l",lwd=1,
     xlim = c(0,52*10),
     ylim = c(0,1300),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))
lines(out4_yr.nb$time,out4_yr.nb$I1*pop_size,col=2,lwd=2,type = "l",lty=2)
lines(out8_yr.nb$time,out8_yr.nb$I1*pop_size,col=3,lwd=2,type = "l",lty=1)
legend(-40,1350, legend = c("0%","40%","80%"),title = "year-round, nb",horiz = T,box.lty = 0,
       col = c(1,2,3),lty=c(1,2,1))
##AG1
plot(out1$time, # plot seasonal
     out1$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     # main= paste("Vaccination fraction =",p),
     col=1,type = "l",lwd=1,
     xlim = c(0,52*10),
     ylim = c(0,1300),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))
lines(out4_yr.AG1$time,out4_yr.AG1$I1*pop_size,col=2,lwd=2,type = "l",lty=2)
lines(out8_yr.AG1$time,out8_yr.AG1$I1*pop_size,col=3,lwd=2,type = "l",lty=1)
legend(-40,1350, legend = c("0%","40%","80%"),title = "year-round, AG1",horiz = T,box.lty = 0,
       col = c(1,2,3),lty=c(1,2,1))
##both
plot(out1$time, # plot seasonal
     out1$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     # main= paste("Vaccination fraction =",p),
     col=1,type = "l",lwd=1,
     xlim = c(0,52*10),
     ylim = c(0,1300),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))
lines(out4_yr.both$time,out4_yr.both$I1*pop_size,col=2,lwd=2,type = "l",lty=2)
lines(out8_yr.both$time,out8_yr.both$I1*pop_size,col=3,lwd=2,type = "l",lty=1)
legend(-40,1350, legend = c("0%","40%","80%"),title = "year-round, both",horiz = T,box.lty = 0,
       col = c(1,2,3),lty=c(1,2,1))
#wk33
##nb
plot(out1$time, # plot seasonal
     out1$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     # main= paste("Vaccination fraction =",p),
     col=1,type = "l",lwd=1,
     xlim = c(0,52*10),
     ylim = c(0,1300),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))
lines(out4_wk33.nb$time,out4_wk33.nb$I1*pop_size,col=2,lwd=2,type = "l",lty=2)
lines(out8_wk33.nb$time,out8_wk33.nb$I1*pop_size,col=3,lwd=2,type = "l",lty=1)
legend(-40,1350, legend = c("0%","40%","80%"),title = "wk33-wk8, nb",horiz = T,box.lty = 0,
       col = c(1,2,3),lty=c(1,2,1))
##AG1
plot(out1$time, # plot seasonal
     out1$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     # main= paste("Vaccination fraction =",p),
     col=1,type = "l",lwd=1,
     xlim = c(0,52*10),
     ylim = c(0,1300),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))
lines(out4_wk33.AG1$time,out4_wk33.AG1$I1*pop_size,col=2,lwd=2,type = "l",lty=2)
lines(out8_wk33.AG1$time,out8_wk33.AG1$I1*pop_size,col=3,lwd=2,type = "l",lty=1)
legend(-40,1350, legend = c("0%","40%","80%"),title = "wk33-wk8, AG1",horiz = T,box.lty = 0,
       col = c(1,2,3),lty=c(1,2,1))
##both
plot(out1$time, # plot seasonal
     out1$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     # main= paste("Vaccination fraction =",p),
     col=1,type = "l",lwd=1,
     xlim = c(0,52*10),
     ylim = c(0,1300),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))
lines(out4_wk33.both$time,out4_wk33.both$I1*pop_size,col=2,lwd=2,type = "l",lty=2)
lines(out8_wk33.both$time,out8_wk33.both$I1*pop_size,col=3,lwd=2,type = "l",lty=1)
legend(-40,1350, legend = c("0%","40%","80%"),title = "wk33-wk8, both",horiz = T,box.lty = 0,
       col = c(1,2,3),lty=c(1,2,1))

#wk37
##nb
plot(out1$time, # plot seasonal
     out1$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     # main= paste("Vaccination fraction =",p),
     col=1,type = "l",lwd=1,
     xlim = c(0,52*10),
     ylim = c(0,1300),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))
lines(out4_wk37.nb$time,out4_wk37.nb$I1*pop_size,col=2,lwd=2,type = "l",lty=2)
lines(out8_wk37.nb$time,out8_wk37.nb$I1*pop_size,col=3,lwd=2,type = "l",lty=1)
legend(-40,1350, legend = c("0%","40%","80%"),title = "wk37-wk8, nb",horiz = T,box.lty = 0,
       col = c(1,2,3),lty=c(1,2,1))
##AG1
plot(out1$time, # plot seasonal
     out1$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     # main= paste("Vaccination fraction =",p),
     col=1,type = "l",lwd=1,
     xlim = c(0,52*10),
     ylim = c(0,1300),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))
lines(out4_wk37.AG1$time,out4_wk37.AG1$I1*pop_size,col=2,lwd=2,type = "l",lty=2)
lines(out8_wk37.AG1$time,out8_wk37.AG1$I1*pop_size,col=3,lwd=2,type = "l",lty=1)
legend(-40,1350, legend = c("0%","40%","80%"),title = "wk37-wk8, AG1",horiz = T,box.lty = 0,
       col = c(1,2,3),lty=c(1,2,1))
##both
plot(out1$time, # plot seasonal
     out1$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     # main= paste("Vaccination fraction =",p),
     col=1,type = "l",lwd=1,
     xlim = c(0,52*10),
     ylim = c(0,1300),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))
lines(out4_wk37.both$time,out4_wk37.both$I1*pop_size,col=2,lwd=2,type = "l",lty=2)
lines(out8_wk37.both$time,out8_wk37.both$I1*pop_size,col=3,lwd=2,type = "l",lty=1)
legend(-40,1350, legend = c("0%","40%","80%"),title = "wk33-wk8, both",horiz = T,box.lty = 0,
       col = c(1,2,3),lty=c(1,2,1))

```

#CEA
##Input Data
```{r CEA, echo=T, eval=F}
#eval = F: preventing running codes

#Run all scenarios and save all in the same folder!
##read multiple files:
library(base)
library(ggplot2)
case <- do.call(rbind, lapply(list.files("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/estimated_case", pattern = ".csv",ignore.case =T,full.names = T), read.csv, header=T))

# write.csv(case,"/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/integrate_files/case_all_scenarios.csv")

CEA <- do.call(rbind, lapply(list.files("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/CEA_analysis", pattern = ".csv",ignore.case =T,full.names = T), read.csv, header=T))
CEA$prevented_case <-CEA$case_base -CEA$case_vac

# write.csv(CEA,"/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/integrate_files/CEA_all_scenarios.csv")

##############################
#Outputs of all interventions
##############################
#Total cases from model prediction : Vaccine coverage =0.2 

cov = 0.6
c_vaccine <- 70     # Cost of vaccine per person 

# Number of infections : yearly
case_base          <- case$case[which(case$vac_str=="seasonal" &case$coverage==0 &case$c==0   &case$vac_week==33)]

case_yr.nb         <- case$case[which(case$vac_str=="year-round" &case$coverage==cov &case$c==cov   &case$vac_week==9)]
case_sea.wk33.nb   <- case$case[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==cov   &case$vac_week==33)]
case_sea.wk37.nb   <- case$case[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==cov   &case$vac_week==37)]

case_yr.AG1        <- case$case[which(case$vac_str=="year-round" &case$coverage==cov &case$c==0   &case$vac_week==9)]
case_sea.wk33.AG1  <- case$case[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==0   &case$vac_week==33)]
case_sea.wk37.AG1  <- case$case[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==0   &case$vac_week==37)]

case_yr.both       <- case$case[which(case$vac_str=="year-round" &case$coverage==cov &case$c==cov/2 &case$vac_week==9)]
case_sea.wk33.both <- case$case[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==cov/2 &case$vac_week==33)]
case_sea.wk37.both <- case$case[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==cov/2 &case$vac_week==37)]
 
############################
#Economic Evaluation
############################
##Costs
c_in  <- 1535          # Cost per inpatient RSV episode (euro 2017)
c_out <- 233           #Cost per outpatient RSV episode (euro 2017)

## 
Belgium_pop <- 11176549      # Belgium pop( average 2011-2018)
target_pop <- 11176549*(1/80)   # Those aged < 1
hos_rate <- 0.011            #RVS-hospitalized <1 yr old (cohort study in UK)
hos_10yr <- hos_rate*target_pop*10
case_10yr <- sum(case_base)
in_rate  <- hos_10yr/case_10yr
## QALY loss  per RSV children < 5 years of age ( Hodgson D,et al.,2020)
QALY_loss_sh <- 0.003823      # QALY loss/RSV(seek health care)
QALY_loss_no_sh <- 0.003024   # QALY loss/RSV(no seek health care)
QALY_loss <- QALY_loss_sh  
##Discoun rate
QALY_dis <- 0.015
cost_dis <- 0.03
QALY_dis_vec <- c()
cost_dis_vec <- c()
for( i in 1:10){
  QALY_dis_vec[i] <- 1/((1+ QALY_dis)^i)
  cost_dis_vec[i] <- 1/((1+ cost_dis)^i)
}


##Check total cost of each strategy with DISCOUNTED
# "real" vaccine coverage: yearly
vac_cov_yr.nb         <- case$real_cov[which(case$vac_str=="year-round" &case$coverage==cov &case$c==cov   &case$vac_week==9)]
vac_cov_sea.wk33.nb   <- case$real_cov[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==cov   &case$vac_week==33)]
vac_cov_sea.wk37.nb   <- case$real_cov[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==cov   &case$vac_week==37)]

vac_cov_yr.AG1        <- case$real_cov[which(case$vac_str=="year-round" &case$coverage==cov &case$c==0   &case$vac_week==9)]
vac_cov_sea.wk33.AG1  <- case$real_cov[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==0   &case$vac_week==33)]
vac_cov_sea.wk37.AG1  <- case$real_cov[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==0   &case$vac_week==37)]

vac_cov_yr.both       <- case$real_cov[which(case$vac_str=="year-round" &case$coverage==cov &case$c==cov/2 &case$vac_week==9)]
vac_cov_sea.wk33.both <- case$real_cov[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==cov/2 &case$vac_week==33)]
vac_cov_sea.wk37.both <- case$real_cov[which(case$vac_str=="seasonal" &case$coverage==cov &case$c==cov/2 &case$vac_week==37)]

# vaccination cost: yearly

vac_cost_yr.nb         <- target_pop*c_vaccine*vac_cov_yr.nb
vac_cost_sea.wk33.nb   <- target_pop*c_vaccine*vac_cov_sea.wk33.nb
vac_cost_sea.wk37.nb   <- target_pop*c_vaccine*vac_cov_sea.wk37.nb

vac_cost_yr.AG1        <- target_pop*c_vaccine*vac_cov_yr.AG1
vac_cost_sea.wk33.AG1  <- target_pop*c_vaccine*vac_cov_sea.wk33.AG1
vac_cost_sea.wk37.AG1  <- target_pop*c_vaccine*vac_cov_sea.wk37.AG1

vac_cost_yr.both       <- target_pop*c_vaccine*vac_cov_yr.both
vac_cost_sea.wk33.both <- target_pop*c_vaccine*vac_cov_sea.wk33.both
vac_cost_sea.wk37.both <- target_pop*c_vaccine*vac_cov_sea.wk37.both

# Disease cost: yearly

cost_yr_nb       <- case_yr.nb*in_rate*c_in    + case_yr.nb*(1-in_rate)*c_out
cost_sea_wk33_nb <- case_sea.wk33.nb*in_rate*c_in + case_sea.wk33.nb*(1-in_rate)*c_out
cost_sea_wk37_nb <- case_sea.wk37.nb*in_rate*c_in + case_sea.wk37.nb*(1-in_rate)*c_out

cost_yr_AG1       <- case_yr.AG1*in_rate*c_in       + case_yr.AG1*(1-in_rate)*c_out 
cost_sea_wk33_AG1 <- case_sea.wk33.AG1*in_rate*c_in + case_sea.wk33.AG1*(1-in_rate)*c_out
cost_sea_wk37_AG1 <- case_sea.wk37.AG1*in_rate*c_in + case_sea.wk37.AG1*(1-in_rate)*c_out

cost_yr_both       <- case_yr.both*in_rate*c_in       + case_yr.both*(1-in_rate)*c_out 
cost_sea_wk33_both <- case_sea.wk33.both*in_rate*c_in + case_sea.wk33.both*(1-in_rate)*c_out
cost_sea_wk37_both <- case_sea.wk37.both*in_rate*c_in + case_sea.wk37.both*(1-in_rate)*c_out

# Total cost: 10 years
Total_cost_base     <- sum((case_base*in_rate*c_in + case_base*(1-in_rate)*c_out)*cost_dis_vec)

Total_cost_yr_nb       <- sum((cost_yr_nb      + vac_cost_yr.nb )     *cost_dis_vec)
Total_cost_sea_wk33_nb <- sum((cost_sea_wk33_nb + vac_cost_sea.wk33.nb)*cost_dis_vec)
Total_cost_sea_wk37_nb <- sum((cost_sea_wk37_nb + vac_cost_sea.wk37.nb)*cost_dis_vec)

Total_cost_yr_AG1       <- sum((cost_yr_AG1       + vac_cost_yr.AG1)      *cost_dis_vec)
Total_cost_sea_wk33_AG1 <- sum((cost_sea_wk33_AG1 + vac_cost_sea.wk33.AG1)*cost_dis_vec)
Total_cost_sea_wk37_AG1 <- sum((cost_sea_wk37_AG1 + vac_cost_sea.wk37.AG1)*cost_dis_vec)

Total_cost_yr_both       <- sum((cost_yr_both       + vac_cost_yr.both)      *cost_dis_vec)
Total_cost_sea_wk33_both <- sum((cost_sea_wk33_both + vac_cost_sea.wk33.both)*cost_dis_vec)
Total_cost_sea_wk37_both <- sum((cost_sea_wk37_both + vac_cost_sea.wk37.both)*cost_dis_vec)                     

############################
#Cost-Effectiveness analysis
############################
# No intervention vs ....
  
#Incremental cost due to vaccination : 10 years
Inc_cost_yr_nb       <- Total_cost_yr_nb - Total_cost_base
Inc_cost_sea_wk33_nb <- Total_cost_sea_wk33_nb - Total_cost_base  
Inc_cost_sea_wk37_nb <- Total_cost_sea_wk37_nb - Total_cost_base  

Inc_cost_yr_AG1       <- Total_cost_yr_AG1 - Total_cost_base
Inc_cost_sea_wk33_AG1 <- Total_cost_sea_wk33_AG1 - Total_cost_base  
Inc_cost_sea_wk37_AG1 <- Total_cost_sea_wk37_AG1 - Total_cost_base  

Inc_cost_yr_both       <- Total_cost_yr_both - Total_cost_base
Inc_cost_sea_wk33_both <- Total_cost_sea_wk33_both - Total_cost_base  
Inc_cost_sea_wk37_both <- Total_cost_sea_wk37_both - Total_cost_base  

# Prevented cases: yearly
Prevented_case_yr_nb       <- case_base - case_yr.nb
Prevented_case_sea_wk33_nb <- case_base - case_sea.wk33.nb 
Prevented_case_sea_wk37_nb <- case_base - case_sea.wk37.nb

Prevented_case_yr_AG1       <- case_base - case_yr.AG1
Prevented_case_sea_wk33_AG1 <- case_base - case_sea.wk33.AG1 
Prevented_case_sea_wk37_AG1 <- case_base - case_sea.wk37.AG1

Prevented_case_yr_both       <- case_base - case_yr.both
Prevented_case_sea_wk33_both <- case_base - case_sea.wk33.both
Prevented_case_sea_wk37_both <- case_base - case_sea.wk37.both

#QALY gained: 10 year = case averted* QALY_loss
QALY_gained_yr_nb <- (sum(case_base) - sum(case_yr.nb))*QALY_loss 
QALY_gained_sea_wk33_nb <- (sum(case_base) - sum(case_sea.wk33.nb))*QALY_loss  
QALY_gained_sea_wk37_nb <- (sum(case_base) - sum(case_sea.wk37.nb))*QALY_loss

QALY_gained_yr_AG1 <- (sum(case_base) - sum(case_yr.AG1))*QALY_loss 
QALY_gained_sea_wk33_AG1 <- (sum(case_base) - sum(case_sea.wk33.AG1))*QALY_loss  
QALY_gained_sea_wk37_AG1 <- (sum(case_base) - sum(case_sea.wk37.AG1))*QALY_loss  

QALY_gained_yr_both <- (sum(case_base) - sum(case_yr.both))*QALY_loss 
QALY_gained_sea_wk33_both <- (sum(case_base) - sum(case_sea.wk33.both))*QALY_loss  
QALY_gained_sea_wk37_both <- (sum(case_base) - sum(case_sea.wk37.both))*QALY_loss 

# ICER per QALY gained: 10 year
ICER_yr_nb         <- Inc_cost_yr_nb       / QALY_gained_yr_nb
ICER_sea_wk33_nb   <- Inc_cost_sea_wk33_nb / QALY_gained_sea_wk33_nb 
ICER_sea_wk37_nb   <- Inc_cost_sea_wk37_nb / QALY_gained_sea_wk37_nb 

ICER_yr_AG1        <- Inc_cost_yr_AG1       / QALY_gained_yr_AG1
ICER_sea_wk33_AG1  <- Inc_cost_sea_wk33_AG1 / QALY_gained_sea_wk33_AG1 
ICER_sea_wk37_AG1  <- Inc_cost_sea_wk37_AG1 / QALY_gained_sea_wk37_AG1

ICER_yr_both       <- Inc_cost_yr_both       / QALY_gained_yr_both
ICER_sea_wk33_both <- Inc_cost_sea_wk33_both / QALY_gained_sea_wk33_both 
ICER_sea_wk37_both <- Inc_cost_sea_wk37_both / QALY_gained_sea_wk37_both 

# ICER per prevented case: 10 years
ICER_p.case_yr_nb         <- Inc_cost_yr_nb       / sum(Prevented_case_yr_nb)
ICER_p.case_sea_wk33_nb   <- Inc_cost_sea_wk33_nb / sum(Prevented_case_sea_wk33_nb)
ICER_p.case_sea_wk37_nb   <- Inc_cost_sea_wk37_nb / sum(Prevented_case_sea_wk37_nb) 

ICER_p.case_yr_AG1        <- Inc_cost_yr_AG1       / sum(Prevented_case_yr_AG1 )
ICER_p.case_sea_wk33_AG1  <- Inc_cost_sea_wk33_AG1 / sum(Prevented_case_sea_wk33_AG1)
ICER_p.case_sea_wk37_AG1  <- Inc_cost_sea_wk37_AG1 / sum(Prevented_case_sea_wk37_AG1)

ICER_p.case_yr_both       <- Inc_cost_yr_both       / sum(Prevented_case_yr_both)
ICER_p.case_sea_wk33_both <- Inc_cost_sea_wk33_both / sum(Prevented_case_sea_wk33_both)
ICER_p.case_sea_wk37_both <- Inc_cost_sea_wk37_both / sum(Prevented_case_sea_wk37_both)

# 
All_res<-matrix(NA, ncol=10, nrow=9)

All_res[1,]<-c(Total_cost_yr_nb       , Total_cost_base, Inc_cost_yr_nb       , QALY_gained_yr_nb       , ICER_yr_nb       , ICER_p.case_yr_nb       ,vac_cov_yr.nb[1] ,sum(case_yr.nb*in_rate*c_in*cost_dis_vec) ,sum(case_base) , sum(case_yr.nb))
All_res[2,]<-c(Total_cost_sea_wk33_nb , Total_cost_base, Inc_cost_sea_wk33_nb , QALY_gained_sea_wk33_nb , ICER_sea_wk33_nb , ICER_p.case_sea_wk33_nb ,vac_cov_sea.wk33.nb[1] ,sum(case_sea.wk33.nb*in_rate*c_in*cost_dis_vec) ,sum(case_base) , sum(case_sea.wk33.nb) )
All_res[3,]<-c(Total_cost_sea_wk37_nb , Total_cost_base, Inc_cost_sea_wk37_nb , QALY_gained_sea_wk37_nb , ICER_sea_wk37_nb , ICER_p.case_sea_wk37_nb ,vac_cov_sea.wk37.nb[1] , sum(case_sea.wk37.nb*in_rate*c_in*cost_dis_vec) ,sum(case_base) , sum(case_sea.wk37.nb))

All_res[4,]<-c(Total_cost_yr_AG1       , Total_cost_base , Inc_cost_yr_AG1       , QALY_gained_yr_AG1       , ICER_yr_AG1       ,ICER_p.case_yr_AG1       ,vac_cov_yr.AG1[1] , sum(case_yr.AG1*in_rate*c_in*cost_dis_vec) , sum(case_base) , sum(case_yr.AG1))
All_res[5,]<-c(Total_cost_sea_wk33_AG1 , Total_cost_base , Inc_cost_sea_wk33_AG1 , QALY_gained_sea_wk33_AG1 , ICER_sea_wk33_AG1 ,ICER_p.case_sea_wk33_AG1 ,vac_cov_sea.wk33.AG1[1] ,sum(case_sea.wk33.AG1*in_rate*c_in*cost_dis_vec) ,sum(case_base) , sum(case_sea.wk33.AG1))
All_res[6,]<-c(Total_cost_sea_wk37_AG1 , Total_cost_base , Inc_cost_sea_wk37_AG1 , QALY_gained_sea_wk37_AG1 , ICER_sea_wk37_AG1 ,ICER_p.case_sea_wk37_AG1 ,vac_cov_sea.wk37.AG1[1] , sum(case_sea.wk37.AG1*in_rate*c_in*cost_dis_vec) ,sum(case_base) , sum(case_sea.wk37.AG1))

All_res[7,]<-c(Total_cost_yr_both       , Total_cost_base , Inc_cost_yr_both       , QALY_gained_yr_both       , ICER_yr_both       , ICER_p.case_yr_both       ,vac_cov_yr.both[1] ,sum(case_yr.both*in_rate*c_in*cost_dis_vec) ,sum(case_base) , sum(case_yr.both))
All_res[8,]<-c(Total_cost_sea_wk33_both , Total_cost_base , Inc_cost_sea_wk33_both , QALY_gained_sea_wk33_both , ICER_sea_wk33_both , ICER_p.case_sea_wk33_both ,vac_cov_sea.wk33.both[1] ,sum(case_sea.wk33.both*in_rate*c_in*cost_dis_vec) ,sum(case_base) , sum(case_sea.wk33.both))
All_res[9,]<-c(Total_cost_sea_wk37_both , Total_cost_base , Inc_cost_sea_wk37_both , QALY_gained_sea_wk37_both , ICER_sea_wk37_both , ICER_p.case_sea_wk37_both ,vac_cov_sea.wk37.both[1], sum(case_sea.wk37.both*in_rate*c_in*cost_dis_vec) ,sum(case_base) , sum(case_sea.wk37.both))
 
colnames(All_res)<-c("Cost_intervention","Cost_no_vaccination","Incremental_Cost", "QALY_gained", "ICER","ICER_pre.case","real_cov","inpatient_cost","case_base","case_vac")
rownames(All_res)<-c("nb_yr","nb_wk33","nb_wk37",
                     "AG1_yr","AG1_wk33","AG1_wk37",
                      "both_yr","both_wk33","both_wk37")
                   
All_res
All_res <- as.data.frame(All_res)
All_res$vac_str <- rownames(All_res)
All_res$vac_str <- as.factor(All_res$vac_str)
All_res$coverage <- cov
All_res$cost_perdose <- c_vaccine
All_res$vac_dose <- All_res$real_cov*target_pop  #1 year
All_res$vac_cost <- All_res$vac_dose* All_res$cost_perdose*sum(cost_dis_vec)
All_res$disease_cost <- All_res$Cost_intervention - All_res$vac_cost
All_res$outpatient_cost <- All_res$disease_cost - All_res$inpatient_cost 

All_res$vac_cost[8] +All_res$outpatient_cost[8] + All_res$inpatient_cost[8]- $Cost_intervention[8]
  


write.csv(All_res,paste("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/CEA_analysis/CEA coverage",cov,"vac_cost",c_vaccine,".csv"))

mil<-1000000
WTP <-35000
my_slope <- WTP/mil # WTP
ggplot(All_res, aes(QALY_gained,Incremental_Cost/mil,color=vac_str,shape=vac_str))+
  geom_point()+
  ggtitle("CEA of immunization strategy for RSV ")+
  ylab (" Incremental cost ( mil.€ ) ")+
  scale_color_manual(values=c(rep(1,3), rep(3,3), rep(4, 3)), name="Vaccination strategy")+
  scale_shape_manual(values=rep(0:2, 3), name="Vaccination strategy")+
  geom_hline(yintercept = 0)+
  geom_abline(intercept=0, slope = my_slope , lty="dashed",col="red")+
  xlim (0,300)+
  ylim (-1,20)+
  annotate(
    "text",
    x = 150,
    y = 150 * my_slope*1.1,
    angle = atan(my_slope) * 1500/pi, # mannually adjust the numerator/pi
    label = "Willlingness to pay (WTP)"
  )+
  theme(legend.title = element_text(face = "bold", size=14),
        plot.title = element_text(size=12, hjust=0.5),
        axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face="bold"))

## Cost of vaccine when Inc_cost_sea_wk37_both =0 => Total_cost_sea_wk37_both = Total_cost_base 

c_vaccine_base <- (Total_cost_base - sum(cost_sea_wk37_both))/sum((target_pop*vac_cov_sea.wk37.both *cost_dis_vec))
c_vaccine_base

```

### ICER vs vaccine cost
```{r vaccine cost, eval=F }
#eval = F: preventing running codes


##read multiple files:
library(base)
library(ggplot2)

CEA <- do.call(rbind, lapply(list.files("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/CEA_analysis", pattern = ".csv",ignore.case =T,full.names = T), read.csv, header=T))
CEA$prevented_case <-CEA$case_base -CEA$case_vac

#####################################
# PSA analysis: Deterministic:choose values for one while keeping the rest constant
#####################################
# Baseline vaccine cost is €37.08/dose RotaTEQ and €55.62/dose RotaRIX
#Sensitivity for vaccination stategy () to changes in vaccination costs per dose in the baseline (health care payer perspective)
# x vs. y : % change from baseline vaccine cost per dose vs. costs per QALY gained

#New facet label names for coverage variable
cov.labs <- c("Coverage = 0.4","Coverage = 0.8") # new name
names(cov.labs) <- c("0.4","0.8") # old name

ggplot(CEA,aes(cost_perdose,ICER/1000,color=vac_str, shape=vac_str))+
  geom_line()+
  geom_point()+
  # ggtitle("CEA of immunization strategy for RSV ")+
   ylab ("Incremental cost per QALY gained (000.€) ")+
   xlab ("Vaccine cost per dose (€)")+
  scale_color_manual(values=c(rep(1,3), rep(3,3), rep(4, 3)), name="Vaccination strategy")+
  scale_shape_manual(values=rep(0:2, 3), name="Vaccination strategy")+
  facet_grid(.~coverage,
             labeller = labeller(coverage=cov.labs))+
  # geom_hline(yintercept = 35000/1000)+
  geom_abline(intercept=35000/1000, slope = 0 , lty="dashed",col="red")+
  # xlim (0,300)+
  # ylim (-15,30)+
  annotate(
    "text",
    x = 10,
    y = 40,
    angle = 0, # mannually adjust the numerator/pi
    label = "WTP"
  )+
  theme_bw()+   # change the background
  theme(legend.title = element_text(face = "bold", size=12),
        plot.title = element_text(size=12, hjust=0.5),
        axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face="bold"),
        strip.text = element_text(size=12, face = "bold"))



```


### Incremental cost vs vaccine cost
```{r vaccine cost, eval =F }
#eval = F: preventing running codes

##read multiple files:
library(base)
library(ggplot2)

CEA <- do.call(rbind, lapply(list.files("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/CEA_analysis", pattern = ".csv",ignore.case =T,full.names = T), read.csv, header=T))

#####################################
# PSA analysis: Deterministic:choose values for one while keeping the rest constant
#####################################
# Baseline vaccine cost is €37.08/dose RotaTEQ and €55.62/dose RotaRIX
#Sensitivity for vaccination stategy () to changes in vaccination costs per dose in the baseline (health care payer perspective)
# x vs. y : % change from baseline vaccine cost per dose vs. costs per QALY gained

#New facet label names for coverage variable
cov.labs <- c("Coverage = 0.4","Coverage = 0.8") # new name
names(cov.labs) <- c("0.4","0.8") # old name

ggplot(CEA[which(CEA$cost_perdose!=0),],aes(cost_perdose,Incremental_Cost/1000000,color=vac_str, shape=vac_str))+
  geom_line()+
  geom_point()+
  # ggtitle("CEA of immunization strategy for RSV ")+
   ylab ("Incremental_Cost (mil.€)")+
   xlab ("Vaccine cost per dose (€)")+
  scale_color_manual(values=c(rep(1,3), rep(3,3), rep(4, 3)), name="Vaccination strategy")+
  scale_shape_manual(values=rep(0:2, 3), name="Vaccination strategy")+
  facet_grid(.~coverage,
             labeller = labeller(coverage=cov.labs))+
  # geom_hline(yintercept = 35000/1000)+
  # geom_abline(intercept=35000/1000, slope = 0 , lty="dashed",col="red")+
  # xlim (0,300)+
  # ylim (-15,30)+
  # annotate(
  #   "text",
  #   x = 150,
  #   y = 150 * my_slope*1.1,
  #   angle = atan(my_slope) * 1500/pi, # mannually adjust the numerator/pi
  #   label = "Willlingness to pay (WTP)"
  # )+
  theme(legend.title = element_text(face = "bold", size=12),
        plot.title = element_text(size=12, hjust=0.5),
        axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face="bold"),
        strip.text = element_text(size=12,face = "bold"))



```


###CEA plane
```{r CEA plane,eval=F}

#eval = F: preventing running codes

#Run all scenarios and save all in the same folder!
##read multiple files:
library(base)
library(ggplot2)

CEA <- do.call(rbind, lapply(list.files("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/CEA_analysis", pattern = ".csv",ignore.case =T,full.names = T), read.csv, header=T))
CEA$prevented_case <-CEA$case_base -CEA$case_vac


#New facet label names for coverage variable
cov.labs <- c("Coverage = 0.4","Coverage = 0.8") # new name
cost.labs <- c("1dose = 35€","1dose = 45€","1dose = 50€")
names(cov.labs) <- c("0.4","0.8") # old name tobe replace
names(cost.labs) <- c("35","45","50")

mil<-1000000
WTP <- 35000
my_slope <- WTP/mil # WTP 

ggplot(CEA[which(CEA$cost_perdose==35|
                 CEA$cost_perdose==45|
                 CEA$cost_perdose==50 ),], aes(QALY_gained,Incremental_Cost/mil,color=vac_str,shape=vac_str))+
  geom_point()+
  # ggtitle("CEA of immunization strategy for RSV ")+
   ylab (" Incremental cost ( mil.€ ) ")+
  scale_color_manual(values=c(rep(1,3), rep(3,3), rep(4, 3)), name="Vaccination strategy")+ 
  scale_shape_manual(values=rep(0:2, 3), name="Vaccination strategy")+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_abline(intercept=0, slope = my_slope , lty="dashed",col="red")+
  facet_grid(cost_perdose~coverage,
             labeller = labeller(cost_perdose=cost.labs,coverage=cov.labs))+
  xlim (0,300)+
  ylim (-10,40)+
  annotate(
    "text",
    x = 150,
    y = 150 * my_slope*1.1,
    angle = atan(my_slope) * 1500/pi, # mannually adjust the numerator/pi
    label = " "
  )+
  theme_bw()+   # change the background
  theme(legend.title = element_text(face = "bold", size=12),
        plot.title = element_text(size=12, hjust=0.5),
        axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face="bold"),
        strip.text = element_text(size=12,face="bold"))


```



