---
title: "Modelling for RSV"
author: "Phuong Huynh Thi"
date: "24/03/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Setting
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())
setwd("/home/phuong/phuonght/gitKraken_project/RSV")
library(deSolve)
library(ggplot2)

#Changeable variables  ##########################
#vaccinnation coverage = c+c1 ( 40%, 80%,)
coverage = 0# 0.2,0.4,0.6,0.8,1
c = coverage*1       # vaccinate a fraction p of newborn 
c1= coverage-c       # vaccinate a fraction p of AG1 ( aged< 1 year)
e = 0.7              # vaccine efficacy is 70%
t_shift = 200        # optimized from fitting# this change up to what fitted set of params
t_vac = 37           # wk29,33,37,9## vaccinating 3,2,1 month before the epidemic season starts at week 41st till the end of the season at wk 8 next year, and year-round (wk9 to wk8).
vac_str = "seasonal" # year-round or seasonal # vaccination strategy will be applied.

#vaccine duration: 32, 28, 24 and 52 weeks are generalized as below: 
vac_period <- (52-t_vac+1+8)  # start vaccination from week 't_vac" this year to week 8 next year # 
vac_rate <- 1/vac_period
report_rate <- 0.675   #assuming only 67.5% of RVS incidence are reported with those aged < 1


```

# Parameters
```{r}
######################################### #
# POPULATION AND PARAMETERS  ----
######################################### #
#https://steemit.com/science/@fouad/x-history-of-math-symbols
pop_size          <- 11176549# Belgium pop size (average 2011-2018)
ag1_size          <- pop_size*1/80
ag2_size          <- pop_size - ag1_size
num_days          <- 500
num_weeks         <- 52*30
num_days_infected <- 10  #[ 8-11], 6.7 is original estimate
num_days_exposed  <- 4   # [2,6]
num_days_waning   <- 200 # [148, 164] best fit
infected_seeds    <- 100# ? 1= 1000 1% of children ??? 

# the fitted parameters may be different between population size
  # set parameters
  params     <- c(sigma = 7/num_days_exposed,  #latent to infectious stage
                  # sigma = 1/0.57,              # latent to infectious stage
                  gamma = 7/num_days_infected,# recovery rate
                  # gamma = 1/1.4,               # recovery rate
                  # nu=  7/num_days_waning,     # rate of loss of immunity
                  nu=  0.03,                  # rat e of loss of immunity
                  eta1 = 1/(1*52),             # aging rate AG1
                  eta2 = 1/(79*52),            # aging rate AG2
                  mu = 1/(80*52),              # birth rate
                  a = 0.84,                    # the degree of seasonality, range [0,1]
                  phi = 3.409,                 # phase shift?
                  b = 1.813,                   #average transmission rate
                  delta = 0.65,                # scaled susceptibility
                  alpha = 0.65                 # scaled infectiousness
  )
# Best fit parameter:
  
  
```

# SEIRS with differnt intervention scenarios.
*Vaccination period*
 - Seasonal : 1 or 2 months befor the season start
 - year-round
*Vaccination target*
 - newborn (maternal)
 - infant ( aged < 1)
 - both
*Vaccine coverage*
 - 40%
 - 80%
```{r Model structure, echo=T, eval=T}
#eval = F: preventing running codes

  #sum total population =1
  S1 <- 1/80 # less than 1 yrs old
  E1 <- (infected_seeds*0.7)/(pop_size)
  I1 <- 0
  R1 <- 0
  V1  <- 0
  E2 <- (infected_seeds*0.3)/(pop_size) # greater than 1 yrs old
  I2 <- 0
  R2 <- 0
  S2 <- 1-S1-E1-I1-R1-E2-I2-R2-V1 

######################################### #
# SET FUNCTION PARAMETERS            ----
######################################### #
# set time frame
times      <- seq(0, num_weeks, by = 1)
# set initial health states
states     <- c(S1 = S1,E1 = E1, I1 = I1, R1 = R1, V1 = V1,
                S2 = S2,E2 = E2, I2 = I2, R2 = R2)
######################################### #
# CREATE SIRV FUNCTION               ----
######################################### #
# Note: updating the health states over time and keeping track of the changes, is handled by the
# ode-function of the 'deSolve' package.
sirv_func <- function(t, states, params) {
  
  with(as.list(c(states, params)),
       {
         # define variables
         beta <- b*(1+a*cos(2*pi*t/52+phi))
         omega <- 1/vac_period
         
         if(vac_str=="year-round"){
           # vaccinate year-round
           if(t<(t_shift+9)){#start week t_vac= 9
             p  <- 0
             p1 <- 0
           } else if (c==1) { # avoid denominator =0 !
             p  <- c*52*vac_rate
             p1 <- 0
           }else{
             p  <- c*52*vac_rate
             p1 <- c1/(1-c)*vac_rate
           }
         }
           
         if(vac_str=="seasonal"){
           # Vaccinate seasonal: 3,2,1 months before the the epidemic season start
           if(t< (t_shift+t_vac)){# skip 't_vac' wks of 
             p  <- 0
             p1 <- 0
           }
           if(t>= (t_shift +t_vac)){# start vaccination epidemic season 2011/2012
             t_week = (t-t_shift)%%52
             if(floor(t_week) >= t_vac|floor(t_week) <= 8){
               if(c==1){
                 p  <- c*52*vac_rate  # scaling dose if vaccination time is shorter?
                 p1 <- 0
               }else{
                 p  <- c*52*vac_rate  # scaling dose if vaccination time is shorter?
                 p1 <- c1/(1-c)*vac_rate
               }
             }else{
               p  <- 0
               p1 <- 0
             }
           } 
         }
         
         # calculate state changes
         dS1 <- (1-p*e)*mu  - beta*S1*(I1+alpha*I2)  + nu*R1                - eta1*S1 - p1*e*S1
         dE1 <-               beta*S1*(I1+alpha*I2)  - sigma*E1             - eta1*E1
         dI1 <-                                        sigma*E1  - gamma*I1 - eta1*I1
         dR1 <-                                      - nu*R1     + gamma*I1 - eta1*R1 
         
         dV1 <- p*e*mu - eta1*V1 + p1*e*S1
         
         dS2 <- eta1*V1 +eta1*S1 - delta*beta*S2*(I1+alpha*I2) + nu*R2                - eta2*S2 
         dE2 <-          eta1*E1 + delta*beta*S2*(I1+alpha*I2) - sigma*E2             - eta2*E2 
         dI2 <-          eta1*I1                               + sigma*E2 - gamma*I2  - eta2*I2 
         dR2 <-          eta1*R1                               - nu*R2    + gamma*I2  - eta2*R2 
         
         # return (dS, dI, dR) as a vector in a list (required for the 'solve' function)
         return(list(c(dS1, dE1, dI1, dR1,dV1, dS2, dE2, dI2, dR2)))
       }
  )
}


```

#ODE
```{r ODE, echo=T, eval=T}
#eval = F: preventing running codes
######################################### #
# SOLVE ODE                          ----
######################################### #
# use the 'ode' function of deSolve package with our SIR function, health states and parameters
out <- ode(func = sirv_func, y = states, times = times, parms = params)
# plot(out)
# summary(out)
# times_output <- seq(num_weeks-(52*8)-2,num_weeks,1)# burning time ## shifting peaks
times_output <- seq(num_weeks-(num_weeks-t_shift),num_weeks,1)# burning time ## shifting peaks
# times_output <- times_output[1:346]# take exactly 8 years (378-32 wks) for later fitting data
times_output <- times_output[1:(52*11)]# show model in 11 yrs
out <- out[out[,1] %in% times_output,] # skip the initial time points
out[,1] <- out[,1] - min(out[,1]-1)# rescale time points ## -1: first week is 1
######################################### #
# PLOT RESULTS                       ----
######################################### #
# convert the 'out' matrix into a data-frame (to enable the use of '$' to access a column by name)
out <- as.data.frame(out)
out$S <- out[,"S1"] + out[,"S2"]
out$E <- out[,"E1"] + out[,"E2"]
out$I <- out[,"I1"] + out[,"I2"]
out$R <- out[,"R1"] + out[,"R2"]
out$V <- out[,"V1"]
pop <- out$S + out$E +out$I + out$R + out$V

##Number of infection each epidemic year : week 33 to week 32 next year:
ag1_est_year1 <- sum(floor(out$I1[33:(33+51)]*pop_size))#year 2011-2012
ag1_est_year2 <- sum(floor(out$I1[85:(85+51)]*pop_size))
ag1_est_year3 <- sum(floor(out$I1[137:(137+51)]*pop_size))
ag1_est_year4 <- sum(floor(out$I1[189:(189+51)]*pop_size))
ag1_est_year5 <- sum(floor(out$I1[241:(241+51)]*pop_size))
ag1_est_year6 <- sum(floor(out$I1[293:(293+51)]*pop_size))
ag1_est_year7 <- sum(floor(out$I1[345:(345+51)]*pop_size))
ag1_est_year8 <- sum(floor(out$I1[397:(397+51)]*pop_size))
ag1_est_year9 <- sum(floor(out$I1[449:(449+51)]*pop_size))
ag1_est_year10 <- sum(floor(out$I1[501:(501+51)]*pop_size))

case <- data.frame(c(ag1_est_year1,
                    ag1_est_year2,
                    ag1_est_year3,
                    ag1_est_year4,
                    ag1_est_year5,
                    ag1_est_year6,
                    ag1_est_year7,
                    ag1_est_year8,
                    ag1_est_year9,
                    ag1_est_year10))


case$year <- seq(1:10)
colnames(case)      <- c("case","year")
#Add other variables
case$coverage <- coverage
case$c        <-c
case$c1       <-c1
case$vac_str  <- vac_str
case$vac_week <- t_vac

#Total number of infections
ag1_est <- floor(out$I1[33:552]*pop_size)# 10 epidemic years
ag1_est_10yr <- sum(ag1_est)
ag1_est_378wk <-sum(floor(out$I1[1:378]*pop_size))
# #saving file
# if(vac_str=="seasonal"){
#   write.csv(case, paste("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/estimated_case/case.est c=",c,"c1=",c1,vac_str,"wk",t_vac,".csv"),row.names = F)
# }
# if(vac_str=="year-round"){
#   write.csv(case, paste("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/estimated_case/case.est c=",c,"c1=",c1,vac_str,".csv"),row.names = F)
# }


#BELGIUM DATA-----------------
case_dt <- read.csv("./RSV data/RSV_cases_time_epistat.csv")
case_dt$week      <- seq(1,dim(case_dt)[1])
age_dt <- read.csv("./RSV data/RSV_cases_age_epistat.csv")
# total cases: 63301,4yrs: 822,3yr:1794,2yr:4559 1yr:13751,0yr:42375
pro.less1yr  <- age_dt$cases[age_dt$age==0] / sum(age_dt$cases) 
case_dt$cases_ag1 <- round(case_dt$cases*pro.less1yr)
case_dt$cases_ag2 <- case_dt$cases - case_dt$cases_ag1
#Assuming only 67.5% incidence was reported
case_dt$cases_scaled <- round(case_dt$cases/0.675)
case_dt$cases_ag1_scaled <- round(case_dt$cases_ag1/0.675)
case_dt$cases_ag2_scaled <- case_dt$cases_scaled - case_dt$cases_ag1_scaled
  
######################################### #
# Plot Model fit                      ----
######################################### #
# plot real data
par(mfrow = c(1,1))
plot(case_dt$week, # plot seasonal 
     case_dt$cases_ag1,
     xlab = "Time (weeks)",
     ylab = "Number of RSV reported",
     pch=19,col=1,
     ylim = c(0, max(case_dt$cases_ag1)*1.2),
     xaxt="none")# for later customizing
axis(1,seq(0,350,by=50))# customize x-axis
# plot initial model
lines(out$time[1:length(case_dt$cases_ag1)],out$I1[1:length(case_dt$cases_ag1)]*pop_size*report_rate,col=2,lwd=2,type = "b",pch=1)
legend(309,1200, legend = c("observed","model fit"), col = c(1,2),lty=1:2,pch=c(19,1))
# score for initial model
get_sum_of_squares(out$I1[1:length(case_dt$cases)]*pop_size,case_dt$cases_ag1)

# Vaccination effect:
par(mfrow = c(1,1))
plot(out$time, # plot seasonal 
     out$I1*pop_size,
     xlab = "Year",
     ylab = "Number of RSV infection",
     main= paste("Vaccination c =",c,"c1=",c1,vac_str,"wk",t_vac),col=2,type = "l",lwd=2,
     xlim = c(0,52*10),
     xaxt="none")# for later customizing
axis(1, at=seq(0,520,by=52),labels = c(0:10))

# # Vaccination effect
# par(mfrow = c(1,1))
# plot(out$time, # plot seasonal
#      out$I1*pop_size,
#      xlab = "Year",
#      ylab = "Number of RSV infection",
#      main= paste("Vaccination fraction =",p),col=2,type = "l",lwd=2,
#      xlim = c(0,52*10),
#      xaxt="none")# for later customizing
# axis(1, at=seq(0,520,by=52),labels = c(0:10))

```

# Optimizing parameters
##original report data 
###Least square

```{r Fitting, echo=T, eval=F}
#eval = F: preventing running codes
######################################### #
# Parameters optimizations                      ----
######################################### #
# DEFINE HELP FUNCTION TO CALCULATE SUM OF SQUARES
get_sum_of_squares <- function(model_values,ref_values) {
  return(sum(sqrt((model_values-ref_values)^2)))
}
# SET GOAL: to use the optimisation package
library(Rcpp)
library(optimization)
#DEFINE FUNCTION TO RUN ODE WITH PARAMETER VECTOR X
x <- c(1.82, 0.76,2.8,461,0.03) #b[?] a(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days
get_model_output <- function(x){
  # params_fitting
  params_fit = params
  params_fit["b"] = x[1]
  params_fit["a"] = x[2]
  params_fit["phi"] =   x[3]
  time_shift =x[4]
  params_fit["nu"] = x[5]
  # get output
  out <- data.frame(ode(func = sirv_func, y = states, times = seq(0,num_weeks,1), parms = params_fit))
  # shift in time (fill with 0)
  out <- approx(x   = out$time - time_shift,
                y   = out$I1,
                xout = seq(0,num_weeks,1), # only extract y where x in this seq
                rule = 1)  # NAs is returned as it is
  names(out) <- c('time','I1')
  # rescale time points
  out$time <- out$time - min(out$time)
  # return output
  return(out)
}
# HELP FUNCTION TO CALCULATE SUM OF SQUARES GIVEN PARAMETERS 'X'
get_parameter_score <- function(x) {
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  # get model score
  model_score <- get_sum_of_squares(model_out$I1*pop_size,case_dt$cases_ag1)
  # return model score
  return(model_score)
}
# HELP FUNCTION TO VISUALIZE THE MODEL FITTING
plot_model_fit <- function(x){
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  # get model score
  model_score <- get_sum_of_squares(model_out$I1[1:length(case_dt$cases)]*pop_size,case_dt$cases_ag1)
  # plot reference data
  plot(case_dt$week,
       case_dt$cases_ag1,
       ylim = c(0,max(case_dt$cases_ag1)*2),type = "b",pch=19,
       main = paste('score:',round(model_score,digits = 2)))
  # plot initial model
  lines(model_out$time,model_out$I1*pop_size,col=2,lwd=1,type = "b")
}
#Optimizing parameters, by specifing lower and upper values
beta0[?] beta1(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days
opt_param_sa <- optim_sa(fun = get_parameter_score, start = c(1.8,0.1,1,-200,7/350),
                         trace = FALSE,
                         lower = c(1,0,1,-1000,7/350),#
                         upper = c(3,1,3,-100,7/160),
                         control = list(dyn_rf = F,
                                        rf = 1,
                                        t0 = 1000, nlimit = 100, r = 0.6, t_min = 0.1
                         ))$par

opt_param_sa
plot_model_fit(opt_param_sa)
################################# #
#report data 100%----------------
################################# #
# sigma = 1/0.57,gamma = 1/1.4
    # plot_model_fit(c(1.85,0.85,3.1,-357,0.032)) #21605.41
  #sigma = 7/num_days_exposed, gamma = 7/num_days_infected
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.038)) # 20915.97
   # plot_model_fit(c(1.82,0.875,3.1,-462,0.034))# 22313.57
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.039)) # 23207.43
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.036)) # 24552.02
   # plot_model_fit(c(1.82,0.88,3.1,-461,0.037)) # 18337.04 # consider
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.037)) # 21000.11
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.039)) # 23207.43 #
   # plot_model_fit(c(1.82,0.87,3.1,-462,0.036)) # 23207.43 #
   # plot_model_fit(c(1.82,0.88,3.1,-462,0.036)) # 24552.02
   

```

## 67.5% Scaling report data 
### Least square
Assuming 67.5% RSV cases are reported as the same rate of rotavirus.

```{r Fitting, echo=T, eval=F}
#eval = F: preventing running codes

######################################### #
# Parameters optimizations                      ----
######################################### #
# DEFINE HELP FUNCTION TO CALCULATE SUM OF SQUARES
get_sum_of_squares <- function(model_values,ref_values) {
  return(sum(sqrt((model_values-ref_values)^2)))
}
# SET GOAL: to use the optimisation package
library(Rcpp)
library(optimization)
#DEFINE FUNCTION TO RUN ODE WITH PARAMETER VECTOR X
x <- c(1.82, 0.76,2.8,515,0.03) #b[?] a(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days
get_model_output <- function(x){
  # params_fitting
  params_fit = params
  params_fit["b"] = x[1]
  params_fit["a"] = x[2]
  params_fit["phi"] =   x[3]
  time_shift =x[4]
  params_fit["nu"] = x[5]
  # get output
  out <- data.frame(ode(func = sirv_func, y = states, times = seq(0,num_weeks,1), parms = params_fit))
  # shift in time (fill with 0)
  out <- approx(x   = out$time - time_shift,
                y   = out$I1,
                xout = seq(0,num_weeks,1),
                rule = 1) # NAs is returned as it is
  names(out) <- c('time','I1')
  # rescale time points
  out$time <- out$time - min(out$time)
  # return output
  return(out)
}
# HELP FUNCTION TO CALCULATE SUM OF SQUARES GIVEN PARAMETERS 'X'
get_parameter_score <- function(x) {
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  
  ###############
  # COMPARING THE MODEL OUTPUT WITH DATA for each combination (optional)
  plot(case_dt$week,
       case_dt$cases_ag1,
       ylim = c(0,max(case_dt$cases_ag1)*1.2),type = "b",pch=19)
  ## plot initial model
  lines(model_out$time,model_out$I1*pop_size*report_rate,col=2,lwd=1,type = "b")
  ################
  
  # get model score
 model_score <- get_sum_of_squares(model_out$I1[1:length(case_dt$cases_ag1)]*pop_size*report_rate,case_dt$cases_ag1)
  # return model score
  return(model_score)
}
#OPTIMIZING PARAMETERS, by specifing lower and upper values
beta0[?] beta1(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days
fit <- optim_sa(fun = get_parameter_score, start = c(1.8,0.65,3.15,200,7/200),
                trace = FALSE,
                lower = c(1.7,0.1,3,50,7/230),#
                upper = c(2,0.9,4,600,7/160),
                control = list(dyn_rf = F,
                               rf = 1,
                               t0 = 1000, nlimit = 100, r = 0.6, t_min = 0.1
                ))

fit$par

# fit<-optim(c(1.81,0.84,3.4,200,7/200),
#            fn = get_parameter_score,
#            lower = c(1.8,0.8,3.2,100,7/230),#
#            upper = c(2,0.9,4,400,7/160),
#            hessian = TRUE,method=("L-BFGS-B"),
#            control = list(trace=TRUE, maxit=100))
# fit$par

# HELP FUNCTION TO VISUALIZE THE MODEL FITTING
plot_model_fit <- function(x){
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  # get model score
  model_score <- get_sum_of_squares(model_out$I1[1:length(case_dt$cases_ag1)]*pop_size*report_rate,case_dt$cases_ag1)
  # plot reference data
  plot(case_dt$week,
       case_dt$cases_ag1,
       ylim = c(0,max(case_dt$cases_ag1)*2),type = "b",pch=19,
       # xlim=c(0,500),
       main = paste('LS:',round(model_score,digits = 2),
                    "b:",opt_param_sa[1],
                    "a:",opt_param_sa[2],
                    "phi:",opt_param_sa[3],
                    "t_shift:",opt_param_sa[4],
                    "nu:",opt_param_sa[5]))
  # plot initial model
  lines(model_out$time,model_out$I1*pop_size*report_rate,col=2,lwd=1,type = "b")
}

plot_model_fit(fit$par)


# [1]   1.813   0.845   3.280 199.060   0.035 # 17662.05
# [1]   1.833   0.885   3.100 200.780   0.035 # 17318.9

  
```

### Poisson likelihood

```{r Fitting, echo=T, eval=F}
#eval = F: preventing running codes

######################################### #
# Parameters optimizations                      ----
######################################### #

# SET GOAL: to use the optimisation package
library(Rcpp)
library(optimization)
#DEFINE FUNCTION TO RUN ODE WITH PARAMETER VECTOR X
x <- c(log(1.82),log( 0.88),log(3.1),log(461), log(0.037)) #b[?] a(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days
get_model_output <- function(x){
  # params_fitting
  params_fit = params
  params_fit["b"] = exp(x[1])
  params_fit["a"] = exp(x[2])
  params_fit["phi"] =   exp(x[3])
  time_shift = exp(x[4])
  params_fit["nu"] = exp(x[5])
  # get output
  out <- data.frame(ode(func = sirv_func, y = states, times = seq(0,num_weeks,1), parms = params_fit))
  # shift in time (fill with 0)
  out <- approx(x   = out$time - time_shift,
                y   = out$I1,
                xout = seq(0,num_weeks,1),
                rule = 1) # NAs is returned as it is
  names(out) <- c('time','I1')
  # rescale time points
  out$time <- out$time - min(out$time)
  # return output
  return(out)
}


# HELP FUNCTION TO CALCULATE Negative log likelihood GIVEN PARAMETERS 'X'
get_parameter_score <- function(x) {
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  
  ###############
  # COMPARING THE MODEL OUTPUT WITH DATA for each combination (optional)
  plot(case_dt$week,
       case_dt$cases_ag1,
       ylim = c(0,max(case_dt$cases_ag1)*1.2),type = "b",pch=19)
  ## plot initial model
  lines(model_out$time,model_out$I1*pop_size*report_rate,col=2,lwd=1,type = "b")
  ################
  
  L<-matrix(0,nrow=length(case_dt$cases),ncol=1)
  
  #Obtains the likelihood from the model
  L<-dpois(case_dt$cases_ag1,model_out$I1[1:length(case_dt$cases_ag1)]*pop_size*report_rate,log=TRUE)
  
  #Log likelihood
  LL<-sum((1-(L==-Inf))*L,na.rm=TRUE)
  
  #Negative log likelihood
  NLL<--LL
  
  # return model score
  return(NLL)
}

#OPTIMIZING PARAMETERS, by specifing lower and upper values, by specifing lower and upper values
# beta0[?] beta1(0,1],phi[1,2],shifting time, nu[1/160,1/230]#160-230 days


fit<-optim(c(log(1.81),log(0.86),log(3.4),log(200),log(7/200)),
           fn = get_parameter_score,
           lower = c(log(1.8),log(0.85),log(3.1),log(200),log(7/230)),
           upper = c(log(1.85),log(0.9),log(3.6),log(300),log(7/190)),
           hessian = TRUE,method=("L-BFGS-B"),
           control = list(trace=TRUE))

par <- round(exp(fit$par),3)
par

# HELP FUNCTION TO VISUALIZE THE MODEL FITTING
plot_model_fit <- function(x){
  # get model output given the parameters in "x"
  model_out <- get_model_output(x)
  # get model score POSSON LOG LIKELIHOOD
  L<-matrix(0,nrow=length(case_dt$cases),ncol=1)
  
  #Obtains the likelihood from the model
  L<-dpois(case_dt$cases_ag1,model_out$I1[1:length(case_dt$cases)]*pop_size*report_rate,log=TRUE)
  
  #Log likelihood
  LL<-sum((1-(L==-Inf))*L,na.rm=TRUE)
  
  #Negative log likelihood
  NLL<--LL
  model_score <- NLL
  
  # plot reference data
  plot(case_dt$week,
       case_dt$cases_ag1,
       ylim = c(0,max(case_dt$cases_ag1)*1.2),type = "b",pch=19,
       # xlim=c(0,500),
       main = paste('NLL:',round(model_score,digits = 2),
                                 "b:",par[1],
                                 "a:",par[2],
                                 "phi:",par[3],
                                 "t_shift:",par[4],
                                 "nu:",par[5]))
  # plot initial model
  lines(model_out$time,model_out$I1*pop_size*report_rate,col=2,lwd=1,type = "b")
}

plot_model_fit(fit$par)


#[1]  0.6004835 -0.1221676  1.3674025  5.8583174 -3.2601691 #NLL:6863.6
 # ~ 1.82300000   0.88500000   3.92514170 350.13450006   0.03838191
#1.81809030  0.82631195  3.96459003 90.76895906  0.03642838
# [1]   1.87345939   0.97943156   2.99637269 254.24983006   0.03329303 
# [1]   1.83636241   0.85147689   3.34478512 458.66374805   0.03570705
#[1]   1.91130578  0.99921739  3.44664899 95.42278310  0.03679449

################################# #
#calculating the confidence intervals for the parameter estimates:
##################################

fisher_info <- solve(fit$hessian)
prop_sigma <- sqrt(diag(fisher_info))
upper <- exp(fit$par+1.96*prop_sigma)
lower <- exp(fit$par-1.96*prop_sigma)
estimate <- exp(fit$par)
  
```

"These are warnings that result from R searching in parameter values that makedpoisreturn not-a-number (NaN) errors.  In other words, if R tries a value the mean of the poisson distribution thatis negative, then R can’t compute a probability for that, because a negative mean is impossible forcounts.  So dpois informs mle2 of this, and then you see a warning, and R goes back to searchingat other parameter values"

#CEA
```{r CEA, echo=T, eval=F}
#eval = F: preventing running codes

#Run all scenarios and save all in the same folder!
##read multiple files:
library(base)
case <- do.call(rbind, lapply(list.files("/home/phuong/Dropbox/2.Master of Epidemiology_Antwerp/year 2/thesis/data analysis/csv_file/estimated_case", pattern = ".csv",ignore.case =T,full.names = T), read.csv, header=T))

##############################
#Outputs of all interventions
##############################
#Total cases from model prediction : Vaccine coverage =0.2 
c = 0.
c_vaccine <-50         # Cost of vaccine per person 

case_base          <- case$case[which(case$vac_str=="seasonal" &case$coverage==0 &case$c==0   &case$vac_week==29)]
case_yr.nb         <- case$case[which(case$vac_str=="year-round" &case$coverage==c &case$c==c   &case$vac_week==9)]
case_yr.AG1        <- case$case[which(case$vac_str=="year-round" &case$coverage==c &case$c==0   &case$vac_week==9)]
case_yr.both       <- case$case[which(case$vac_str=="year-round" &case$coverage==c &case$c==c/2 &case$vac_week==9)]
case_sea.wk29.nb   <- case$case[which(case$vac_str=="seasonal" &case$coverage==c &case$c==c   &case$vac_week==29)]
case_sea.wk29.AG1  <- case$case[which(case$vac_str=="seasonal" &case$coverage==c &case$c==0   &case$vac_week==29)]
case_sea.wk29.both <- case$case[which(case$vac_str=="seasonal" &case$coverage==c &case$c==c/2 &case$vac_week==29)]
case_sea.wk33.nb   <- case$case[which(case$vac_str=="seasonal" &case$coverage==c &case$c==c   &case$vac_week==33)]
case_sea.wk33.AG1  <- case$case[which(case$vac_str=="seasonal" &case$coverage==c &case$c==0   &case$vac_week==33)]
case_sea.wk33.both <- case$case[which(case$vac_str=="seasonal" &case$coverage==c &case$c==c/2 &case$vac_week==33)]
case_sea.wk37.nb   <- case$case[which(case$vac_str=="seasonal" &case$coverage==c &case$c==c   &case$vac_week==37)]
case_sea.wk37.AG1  <- case$case[which(case$vac_str=="seasonal" &case$coverage==c &case$c==0   &case$vac_week==37)]
case_sea.wk37.both <- case$case[which(case$vac_str=="seasonal" &case$coverage==c &case$c==c/2 &case$vac_week==37)]
 
#Death Outcomes (number of death) 
# risk_death<- 0.05 #...#  #case fatality of hepatitis E
# 
# Total_death_base <- Total_case_base*risk_death      #Total cases from model prediction
# Total_death_lat <- Total_case_lat*risk_death
# Total_death_vac <- Total_case_vac*risk_death#...#
# 
# Total_death_base
# Total_death_lat
# Total_death_vac
############################
#Economic Evaluation
############################
#Costs
c_in  <- 1535          # Cost per inpatient RSV episode (euro 2017)
c_out  <- 23            # Cost per outpatient RSV episode (euro 2017)

#
Belgium_pop <- 11176549      # Belgium pop( average 2011-2018)
target_pop <- 11176549*(1/80)   # Those aged < 1
hos_rate <- 0.011            #RVS-hospitalized <1 yr old (cohort study in UK)
hos_10yr <- hos_rate*target_pop*10
case_10yr <- sum(case_base)
in_rate  <- hos_10yr/case_10yr
# QALY loss  per RSV children < 5 years of age ( Hodgson D,et al.,2020)
QALY_loss_sh <- 0.003823      # QALY loss/RSV(seek health care)
QALY_loss_no_sh <- 0.003024   # QALY loss/RSV(no seek health care)
QALY_loss <- (QALY_loss_sh +QALY_loss_no_sh)/2   
#Discoun rate
QALY_dis <- 0.015
cost_dis <- 0.03
QALY_dis_vec <- c()
cost_dis_vec <- c()
for( i in 1:10){
  QALY_dis_vec[i] <- 1/((1+ QALY_dis)^i)
  cost_dis_vec[i] <- 1/((1+ cost_dis)^i)
}


#Check total cost of each strategy with DISCOUNTED
Total_cost_base     <- sum((case_base*in_rate*c_in + case_base*(1-in_rate)*c_out)*cost_dis_vec)
vaccination_cost <- c(rep(c*target_pop*c_vaccine,10))

Total_cost_yr_nb    <- sum((case_yr.nb*in_rate*c_in + case_yr.nb*(1-in_rate)*c_out + vaccination_cost)*cost_dis_vec)
Total_cost_yr_AG1   <- sum((case_yr.AG1*in_rate*c_in + case_yr.AG1*(1-in_rate)*c_out + vaccination_cost)*cost_dis_vec)
Total_cost_yr_both  <- sum((case_yr.both*in_rate*c_in + case_yr.both*(1-in_rate)*c_out + vaccination_cost)*cost_dis_vec)

Total_cost_sea_wk29_nb <- sum((case_sea.wk29.nb*in_rate*c_in + case_sea.wk29.nb*(1-in_rate)*c_out+ vaccination_cost)*cost_dis_vec)
Total_cost_sea_wk33_nb <- sum((case_sea.wk33.nb*in_rate*c_in + case_sea.wk33.nb*(1-in_rate)*c_out+ vaccination_cost)*cost_dis_vec)
Total_cost_sea_wk37_nb <- sum((case_sea.wk37.nb*in_rate*c_in + case_sea.wk37.nb*(1-in_rate)*c_out+ vaccination_cost)*cost_dis_vec)

Total_cost_sea_wk29_AG1 <- sum((case_sea.wk29.AG1*in_rate*c_in + case_sea.wk29.AG1*(1-in_rate)*c_out+ vaccination_cost)*cost_dis_vec)
Total_cost_sea_wk33_AG1 <- sum((case_sea.wk33.AG1*in_rate*c_in + case_sea.wk33.AG1*(1-in_rate)*c_out+ vaccination_cost)*cost_dis_vec)
Total_cost_sea_wk37_AG1 <- sum((case_sea.wk37.AG1*in_rate*c_in + case_sea.wk37.AG1*(1-in_rate)*c_out+ vaccination_cost)*cost_dis_vec)

Total_cost_sea_wk29_both <- sum((case_sea.wk29.both*in_rate*c_in + case_sea.wk29.both*(1-in_rate)*c_out+ vaccination_cost)*cost_dis_vec)
Total_cost_sea_wk33_both <- sum((case_sea.wk33.both*in_rate*c_in + case_sea.wk33.both*(1-in_rate)*c_out+ vaccination_cost)*cost_dis_vec)
Total_cost_sea_wk37_both <- sum((case_sea.wk37.both*in_rate*c_in + case_sea.wk37.both*(1-in_rate)*c_out+ vaccination_cost)*cost_dis_vec )                      



############################
#Cost-Effectiveness analysis
############################
# No intervention vs ....
  
#Incremental cost due to vaccination : 10 years
Inc_cost_yr_nb <- Total_cost_yr_nb - Total_cost_base
Inc_cost_yr_AG1 <- Total_cost_yr_AG1 - Total_cost_base
Inc_cost_yr_both <- Total_cost_yr_both - Total_cost_base

Inc_cost_sea_wk29_nb <- Total_cost_sea_wk29_nb - Total_cost_base  
Inc_cost_sea_wk33_nb <- Total_cost_sea_wk33_nb - Total_cost_base  
Inc_cost_sea_wk37_nb <- Total_cost_sea_wk37_nb - Total_cost_base  

Inc_cost_sea_wk29_AG1 <- Total_cost_sea_wk29_AG1 - Total_cost_base  
Inc_cost_sea_wk33_AG1 <- Total_cost_sea_wk33_AG1 - Total_cost_base  
Inc_cost_sea_wk37_AG1 <- Total_cost_sea_wk37_AG1 - Total_cost_base  

Inc_cost_sea_wk29_both <- Total_cost_sea_wk29_both - Total_cost_base  
Inc_cost_sea_wk33_both <- Total_cost_sea_wk33_both - Total_cost_base  
Inc_cost_sea_wk37_both <- Total_cost_sea_wk37_both - Total_cost_base  

#QALY gained: 10 year = case averted* QALY_loss
QALY_gained_yr_nb <- (sum(case_base) - sum(case_yr.nb))*QALY_loss 
QALY_gained_yr_AG1 <- (sum(case_base) - sum(case_yr.AG1))*QALY_loss 
QALY_gained_yr_both <- (sum(case_base) - sum(case_yr.both))*QALY_loss 

QALY_gained_sea_wk29_nb <- (sum(case_base) - sum(case_sea.wk29.nb))*QALY_loss  
QALY_gained_sea_wk33_nb <- (sum(case_base) - sum(case_sea.wk33.nb))*QALY_loss  
QALY_gained_sea_wk37_nb <- (sum(case_base) - sum(case_sea.wk37.nb))*QALY_loss

QALY_gained_sea_wk29_AG1 <- (sum(case_base) - sum(case_sea.wk29.AG1))*QALY_loss  
QALY_gained_sea_wk33_AG1 <- (sum(case_base) - sum(case_sea.wk33.AG1))*QALY_loss  
QALY_gained_sea_wk37_AG1 <- (sum(case_base) - sum(case_sea.wk37.AG1))*QALY_loss  

QALY_gained_sea_wk29_both <- (sum(case_base) - sum(case_sea.wk29.both))*QALY_loss  
QALY_gained_sea_wk33_both <- (sum(case_base) - sum(case_sea.wk33.both))*QALY_loss  
QALY_gained_sea_wk37_both <- (sum(case_base) - sum(case_sea.wk37.both))*QALY_loss  


# ICER
ICER_yr_nb<- Inc_cost_yr_nb/QALY_gained_yr_nb
ICER_yr_AG1<- Inc_cost_yr_AG1/QALY_gained_yr_AG1
ICER_yr_both<- Inc_cost_yr_both/QALY_gained_yr_both

ICER_sea_wk29_nb<- Inc_cost_sea_wk29_nb/QALY_gained_sea_wk29_nb 
ICER_sea_wk33_nb<- Inc_cost_sea_wk29_nb/QALY_gained_sea_wk33_nb 
ICER_sea_wk37_nb<- Inc_cost_sea_wk29_nb/QALY_gained_sea_wk37_nb 

ICER_sea_wk29_AG1<- Inc_cost_sea_wk29_AG1/QALY_gained_sea_wk29_AG1 
ICER_sea_wk33_AG1<- Inc_cost_sea_wk29_AG1/QALY_gained_sea_wk33_AG1 
ICER_sea_wk37_AG1<- Inc_cost_sea_wk29_AG1/QALY_gained_sea_wk37_AG1 

ICER_sea_wk29_both<- Inc_cost_sea_wk29_both/QALY_gained_sea_wk29_both 
ICER_sea_wk33_both<- Inc_cost_sea_wk29_both/QALY_gained_sea_wk33_both 
ICER_sea_wk37_both<- Inc_cost_sea_wk29_both/QALY_gained_sea_wk37_both 


# 
All_res<-matrix(NA, ncol=5, nrow=12)

All_res[1,]<-c(Total_cost_yr_nb,       Total_cost_base, Inc_cost_yr_nb,       QALY_gained_yr_nb ,      ICER_yr_nb)
All_res[2,]<-c(Total_cost_sea_wk29_nb, Total_cost_base, Inc_cost_sea_wk29_nb, QALY_gained_sea_wk29_nb, ICER_sea_wk29_nb)
All_res[3,]<-c(Total_cost_sea_wk33_nb, Total_cost_base, Inc_cost_sea_wk33_nb, QALY_gained_sea_wk33_nb, ICER_sea_wk33_nb)
All_res[4,]<-c(Total_cost_sea_wk37_nb, Total_cost_base, Inc_cost_sea_wk37_nb, QALY_gained_sea_wk37_nb, ICER_sea_wk37_nb)

All_res[5,]<-c(Total_cost_yr_AG1,Total_cost_base,Inc_cost_yr_AG1,QALY_gained_yr_AG1 ,ICER_yr_AG1)
All_res[6,]<-c(Total_cost_sea_wk29_AG1,Total_cost_base,Inc_cost_sea_wk29_AG1,QALY_gained_sea_wk29_AG1 ,ICER_sea_wk29_AG1)
All_res[7,]<-c(Total_cost_sea_wk33_AG1,Total_cost_base,Inc_cost_sea_wk33_AG1,QALY_gained_sea_wk33_AG1 ,ICER_sea_wk33_AG1)
All_res[8,]<-c(Total_cost_sea_wk37_AG1,Total_cost_base,Inc_cost_sea_wk37_AG1,QALY_gained_sea_wk37_AG1 ,ICER_sea_wk37_AG1)

All_res[9,]<-c(Total_cost_yr_both,Total_cost_base,Inc_cost_yr_both,QALY_gained_yr_both ,ICER_yr_both)
All_res[10,]<-c(Total_cost_sea_wk29_both,Total_cost_base,Inc_cost_sea_wk29_both,QALY_gained_sea_wk29_both ,ICER_sea_wk29_both)
All_res[11,]<-c(Total_cost_sea_wk33_both,Total_cost_base,Inc_cost_sea_wk33_both,QALY_gained_sea_wk33_both ,ICER_sea_wk33_both)
All_res[12,]<-c(Total_cost_sea_wk37_both,Total_cost_base,Inc_cost_sea_wk37_both,QALY_gained_sea_wk37_both ,ICER_sea_wk37_both)

colnames(All_res)<-c("Cost vaccination","Cost_no_vaccination","Incremental Cost", "QALY gained", "ICER")
rownames(All_res)<-c("yr_nb",
                     "wk29_nb","wk33_nb","wk37_nb","yr_AG1",
                     "wk29_AG1","wk33_AG1","wk37_AG1","yr_both",
                     "wk29_both","wk33_both","wk37_both")
All_res


#Plot to see results on the ICER plane
# plot(All_res[,2], All_res[,1], xlim=c(-1,200), ylim=c(-100,1500000), ylab="Incremental costs ($USD)", xlab="QALY gained", pch=18, col=c("red","brown"), main="CEA of Interventions for HepE")
# text(All_res[,2], All_res[,1],label=c("Latrines","Vaccine"), cex=0.8, pos=3)
# abline(a=0, b=1000, lty=3, col='black')
# abline(v = 0, h = 0)

plot(All_res[,4], All_res[,3]/1000000, xlim=c(-1,2050), ylim=c(-1,5),
     ylab="Incremental costs ( million euro)", xlab="QALY gained", 
     pch=c(1,16,17,18,1,16,17,18,1,16,17,18),
     # col=c(4), # black,red,blue,newborn, AG1, both
     col=c(1,1,1,1,2,2,2,2,4,4,4,4), # black,red,blue:newborn, AG1, both
     main=paste("CEA of Interventions for RSV coverage =",c,"vac_cost =",c_vaccine))

text(All_res[,4], All_res[,3]/1000000,label=c("yr_nb",
                     "w29_nb","w33_nb","w37_nb","yr_AG1",
                     "w29_AG1","w33_AG1","w37_AG1","yr_both",
                     "w29_both","w33_both","w37_both"),
                      cex=0.5, pos=3)
abline(a=0, b=35000/1000000, lty=3, col='black')
abline(v = 0, h = 0)


```


